---
title: 'Generate prediction data'
author: 'Jay Achar'
date: '`r Sys.time()`'
output:
  html_document:
    code_folding: hide
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

suppressMessages(library(tidyverse))
library(here)
library(forecast)
```

```{r load, message=FALSE, warning=FALSE }
files <- list.files(here("R"))
walk(files,
     ~source(here("R", .x)))

const <- constants()

raw <- read_data("notifications")
```

```{r restructure-data}
dd <- prepare_data(raw, const = const)
```

## Missing values

Find all timeseries with missing values to all imputation.

```{r extract-missing-values}
# extract all time series with zero values
missing <- dd$long$country %>%
        filter(iso3 %in% const$high_burden) %>%
        filter(year >= 2014,
               year != 2020,
               age_group != "014") %>%
        mutate(age_group = factor(
                age_group,
                levels = c("04", "514", "15plus"),
                ordered = TRUE
        )) %>%
        select(iso3, year, sex, age_group, cases) %>%
        group_by(iso3, sex, age_group) %>%
        nest() %>%
        filter(map_lgl(data, function(d) {
                any(d$cases == 0 | is.na(d$cases))
        })) %>%
        unnest(cols = c(data)) %>%
        ungroup() %>%
        mutate(cases = ifelse(cases == 0,
                              NA_integer_,
                              cases))

saveRDS(missing,
        file = here::here("artefacts/missing.rds"))

```

```{r handle-missing-data}
clean <- prepare_long_data(dd)
```

## Predict 2020 notifications

Predictions should be performed on the most granular data available.
In this analysis, that is country and regional level data by age group and sex.

```{r create-predicted-data }
# create training data
## remove 2020
forecasts <- bind_rows(clean,
          .id = "type") %>%
  filter(year != 2020) %>%
  group_by(location, age_group, type, sex) %>%
## nest data by location & age group
  nest() %>%
## create time-series
  mutate(ts = map(data,
                  function(series) {
                    select(series, -year) %>%
                      ts(start = 2014, frequency = 1)
                  })) %>%
  forecast_next_year(order = c(2, 0, 0),
                     drift = TRUE,
                     lambda = NULL,
                     log_transform = TRUE)

```

```{r extract-predictions}

predictions <- forecasts %>%
  mutate(prediction = map(forecast, function(series) {
    data.frame(
      point = as.integer(series$point),
      lower95 = as.integer(series$lower95),
      upper95 = as.integer(series$upper95)
    )
  })) %>%
  select(type, location, age_group, sex, prediction) %>%
  unnest(cols = c(prediction))

# required for supp table 4
saveRDS(predictions,
        file = here::here("artefacts/granular_predictions.rds"))
head(predictions)
```

## Calculate variance

```{r calculate-variance}
granular_predictions <- predictions %>%
  mutate(variance = ((upper95 - lower95) / 3.92) ^ 2) %>%
  select(-lower95, -upper95)

```

## Predictions {.tabset .tabset-pills}

### Main Figure 1

```{r aggregate-age-region}
final_prediction <- list()

final_prediction$age_region <- granular_predictions %>%
  filter(type == "region") %>%
  grouped_predictions(age_group, location)

head(final_prediction$age_region)
```

### Main Figure 2

```{r aggregate-age-hbc}
final_prediction$age_hbc <- granular_predictions %>%
  filter(type == "hbc") %>%
  grouped_predictions(age_group, location)

head(final_prediction$age_hbc)
```

### Supplement Table 3

Global age and sex uses WHO regional data

```{r aggregate-age-sex}
temp_age_sex <- granular_predictions %>%
  filter(type == "region") %>%
  grouped_predictions(age_group, sex)

final_prediction$age_sex <- granular_predictions %>%
  filter(type == "region") %>%
  grouped_predictions(age_group) %>%
  mutate(sex = "all") %>%
  select(age_group, sex, point, sd) %>%
  bind_rows(temp_age_sex) %>%
  arrange(age_group, desc(sex))


# calculate 95% CI
final_prediction <- lapply(final_prediction,
                           FUN = function(x) {
                             x$lower95 = x$point - x$sd * 1.96
                             x$upper95 = x$point + x$sd * 1.96
                             x
                           })


saveRDS(final_prediction,
        file = here::here("artefacts/manuscript_predictions.rds"))
head(final_prediction$age_sex)
```

### Supplement Table 4

Uses the same predictions as Main figure 1
