---
title: "Evaluating factors that affected the TB notification-burden gap in 2020"
output: html_notebook
---

Data Frames Required 
- Notification, burden and difference data for 0-4, 5-14, 0-14, 15plus and whole population
- Focusing on the high burden countries 

```{r}
setwd("~/Desktop/AFP/modV3/data")
library(dplyr)
library(tidyverse)
library(magrittr)

 burd_2020 <- read_csv("TB_burden_2020.csv")
 not_2020 <- read_csv("TB_notifications.csv")
 
 burd_04 <- burd_2020 %>% filter(risk_factor == "all") %>% filter(age_group == "0-4")
 burd_514 <- burd_2020 %>% filter(risk_factor == "all") %>% filter(age_group == "5-14")
 burd_014 <- burd_2020 %>% filter(risk_factor == "all") %>% filter(age_group == "0-14")
 burd_15plus <- burd_2020 %>% filter(risk_factor == "all") %>% filter(age_group == "15plus")

 burd_04 <- burd_04[, c(1,3, 9, 11)]
 burd_514 <- burd_514[, c(1,3, 9, 11)]
 burd_014 <- burd_014[, c(1,3, 9, 11)]
 burd_15plus <- burd_15plus[, c(1,3, 9, 11)]
 
 #preparing the final burden data 
 piv_04 <- pivot_wider(burd_04, names_from = sex, values_from = best)
 final_04 <- mutate(piv_04, "total" = f + m)
 piv_514 <- pivot_wider(burd_514, names_from = sex, values_from = best)
 final_514 <- mutate(piv_514, "total" = f + m)
 piv_014 <- pivot_wider(burd_014, names_from = sex, values_from = best)
 piv_014 <- piv_014[, -3]
 final_014 <- mutate(piv_014, "total" = f + m)
 piv_15plus <- pivot_wider(burd_15plus, names_from = sex, values_from = best)
 piv_15plus <- piv_15plus[, -3]
 final_15plus <- mutate(piv_15plus, "total" = f + m)
 
 #preparing the notification data 
 not_2020 %<>% filter(year == 2020)
 not_2020 <- not_2020[, c(1,3,5,100,103,104,113,115,118,119,128)]

 #combining the data frames 
 combined_04 <- cbind(final_04, not_2020$newrel_m04, not_2020$newrel_f04)
 combined_514 <- cbind(final_514, not_2020$newrel_m514, not_2020$newrel_f514)
 combined_014 <- cbind(final_014, not_2020$newrel_m014, not_2020$newrel_f014)
 combined_15plus <- cbind(final_15plus, not_2020$newrel_m15plus, not_2020$newrel_f15plus)

colnames(combined_04) <- c("country", "iso3", "F_est", "M_est", "TOT_est", "m_cases", "f_cases")
colnames(combined_514) <- c("country", "iso3", "F_est", "M_est", "TOT_est", "m_cases", "f_cases")
colnames(combined_014) <- c("country", "iso3", "F_est", "M_est", "TOT_est", "m_cases", "f_cases")
colnames(combined_15plus) <- c("country", "iso3", "F_est", "M_est", "TOT_est", "m_cases", "f_cases")

combined_04 <- mutate(combined_04, "TOT_cases" = m_cases + f_cases)
combined_514 <- mutate(combined_514, "TOT_cases" = m_cases + f_cases)
combined_014 <- mutate(combined_014, "TOT_cases" = m_cases + f_cases)
combined_15plus <- mutate(combined_15plus, "TOT_cases" = m_cases + f_cases)

#data frames consisting of sex disaggregated and total cases and estimate for each age group
dif_tot_04 <- mutate(combined_04, "TOT_dif" = TOT_est - TOT_cases)
dif_tot_514 <- mutate(combined_514, "TOT_dif" = TOT_est - TOT_cases)
dif_tot_014 <- mutate(combined_014, "TOT_dif" = TOT_est - TOT_cases)
dif_tot_15plus <- mutate(combined_15plus, "TOT_dif" = TOT_est - TOT_cases)
dif_tot_all <- merge(dif_tot_15plus, dif_tot_014, by = c("country", "iso3"), all.x = TRUE)
final_tot <- mutate(dif_tot_all, "F_est" = F_est.x + F_est.y, "M_est" = M_est.x + M_est.y, "TOT_est" = TOT_est.x + TOT_est.y, "M_cases" = m_cases.x + m_cases.y, "F_cases" = f_cases.x + f_cases.y, "TOT_cases" = TOT_cases.x + TOT_cases.y, "TOT_dif" = TOT_dif.x + TOT_dif.y)
FINAL_2020 <- final_tot[, c(1,2, 17:23)]
```


Selecting data for 30 high burden countries only

```{r}
top_04 <- dif_tot_04[dif_tot_04$country %in% c("Angola", "Bangladesh", "Brazil", "China", "Democratic People's Republic of Korea", "Democratic Republic of the Congo", "Ethiopia", "India", "Indonesia", "Kenya", "Mozambique", "Myanmar", "Nigeria", "Pakistan", "Philippines", "Russian Federation", "South Africa", "Thailand", "United Republic of Tanzania", "Viet Nam", "Cambodia", "Central African Republic", "Congo", "Lesotho", "Liberia", "Namibia", "Papua New Guinea", "Sierra Leone", "Zambia", "Zimbabwe"), ]

top_514 <- dif_tot_514[dif_tot_514$country %in% c("Angola", "Bangladesh", "Brazil", "China", "Democratic People's Republic of Korea", "Democratic Republic of the Congo", "Ethiopia", "India", "Indonesia", "Kenya", "Mozambique", "Myanmar", "Nigeria", "Pakistan", "Philippines", "Russian Federation", "South Africa", "Thailand", "United Republic of Tanzania", "Viet Nam", "Cambodia", "Central African Republic", "Congo", "Lesotho", "Liberia", "Namibia", "Papua New Guinea", "Sierra Leone", "Zambia", "Zimbabwe"), ]

top_014 <- dif_tot_014[dif_tot_04$country %in% c("Angola", "Bangladesh", "Brazil", "China", "Democratic People's Republic of Korea", "Democratic Republic of the Congo", "Ethiopia", "India", "Indonesia", "Kenya", "Mozambique", "Myanmar", "Nigeria", "Pakistan", "Philippines", "Russian Federation", "South Africa", "Thailand", "United Republic of Tanzania", "Viet Nam", "Cambodia", "Central African Republic", "Congo", "Lesotho", "Liberia", "Namibia", "Papua New Guinea", "Sierra Leone", "Zambia", "Zimbabwe"), ]

top_15plus <- dif_tot_15plus[dif_tot_04$country %in% c("Angola", "Bangladesh", "Brazil", "China", "Democratic People's Republic of Korea", "Democratic Republic of the Congo", "Ethiopia", "India", "Indonesia", "Kenya", "Mozambique", "Myanmar", "Nigeria", "Pakistan", "Philippines", "Russian Federation", "South Africa", "Thailand", "United Republic of Tanzania", "Viet Nam", "Cambodia", "Central African Republic", "Congo", "Lesotho", "Liberia", "Namibia", "Papua New Guinea", "Sierra Leone", "Zambia", "Zimbabwe"), ]

top_tot <- FINAL_tot[FINAL_tot$country %in% c("Angola", "Bangladesh", "Brazil", "China", "Democratic People's Republic of Korea", "Democratic Republic of the Congo", "Ethiopia", "India", "Indonesia", "Kenya", "Mozambique", "Myanmar", "Nigeria", "Pakistan", "Philippines", "Russian Federation", "South Africa", "Thailand", "United Republic of Tanzania", "Viet Nam", "Cambodia", "Central African Republic", "Congo", "Lesotho", "Liberia", "Namibia", "Papua New Guinea", "Sierra Leone", "Zambia", "Zimbabwe"), ]

##Adding percentage reported as a column
topp_04 <- mutate(top_04, "perc_tot" = 100 * (TOT_cases/TOT_est))
topp_514 <- mutate(top_514, "perc_tot" = 100 * (TOT_cases/TOT_est))
topp_014 <- mutate(top_014, "perc_tot" = 100 * (TOT_cases/TOT_est))
topp_15plus <- mutate(top_15plus, "perc_tot" = 100 * (TOT_cases/TOT_est))
topp_tot <- mutate(top_tot, "perc_tot" = 100 * (TOT_cases/TOT_est))

```


Percentage reporting of TB cases in 2019

```{r}
setwd("~/Desktop/AFP/Original Data")

burd_2019 <- read_csv("TBburden.csv")
not_2019 <- read_csv("TBnotif.csv")

b19_04 <- burd_2019 %>% filter(risk_factor == "all") %>% filter(age_group == "0-4")
 b19_514 <- burd_2019 %>% filter(risk_factor == "all") %>% filter(age_group == "5-14")
 b19_014 <- burd_2019 %>% filter(risk_factor == "all") %>% filter(age_group == "0-14")
 b19_15plus <- burd_2019 %>% filter(risk_factor == "all") %>% filter(age_group == "15plus")

 b19_04 <- b19_04[, c(1,3, 9, 11)]
 b19_514 <- b19_514[, c(1,3, 9, 11)]
 b19_014 <- b19_014[, c(1,3, 9, 11)]
 b19_15plus <- b19_15plus[, c(1,3, 9, 11)]
 
 #preparing the final burden data 
 p_04 <- pivot_wider(b19_04, names_from = sex, values_from = best)
 f_04 <- mutate(p_04, "total" = f + m)
 p_514 <- pivot_wider(b19_514, names_from = sex, values_from = best)
 f_514 <- mutate(p_514, "total" = f + m)
 p_014 <- pivot_wider(b19_014, names_from = sex, values_from = best)
 p_014 <- p_014[, -3]
 f_014 <- mutate(p_014, "total" = f + m)
 p_15plus <- pivot_wider(b19_15plus, names_from = sex, values_from = best)
 p_15plus <- p_15plus[, -3]
 f_15plus <- mutate(p_15plus, "total" = f + m)
 
 #Preparing notification data 
  not_2019 %<>% filter(year == 2019)
 not_2019 <- not_2019[, c(1,3,5,100,103,104,113,115,118,119,128)]
 
 c_04 <- cbind(f_04, not_2019$newrel_m04, not_2019$newrel_f04)
 c_514 <- cbind(f_514, not_2019$newrel_m514, not_2019$newrel_f514)
 c_014 <- cbind(f_014, not_2019$newrel_m014, not_2019$newrel_f014)
 c_15plus <- cbind(f_15plus, not_2019$newrel_m15plus, not_2019$newrel_f15plus)

colnames(c_04) <- c("country", "iso3", "F_est", "M_est", "TOT_est", "m_cases", "f_cases")
colnames(c_514) <- c("country", "iso3", "F_est", "M_est", "TOT_est", "m_cases", "f_cases")
colnames(c_014) <- c("country", "iso3", "F_est", "M_est", "TOT_est", "m_cases", "f_cases")
colnames(c_15plus) <- c("country", "iso3", "F_est", "M_est", "TOT_est", "m_cases", "f_cases")

c_04 <- mutate(c_04, "TOT_cases" = m_cases + f_cases)
c_514 <- mutate(c_514, "TOT_cases" = m_cases + f_cases)
c_014 <- mutate(c_014, "TOT_cases" = m_cases + f_cases)
c_15plus <- mutate(c_15plus, "TOT_cases" = m_cases + f_cases)

#Adding percentage reported column
dif_04 <- mutate(c_04, "TOT_dif" = TOT_est - TOT_cases)
dif_514 <- mutate(c_514, "TOT_dif" = TOT_est - TOT_cases)
dif_014 <- mutate(c_014, "TOT_dif" = TOT_est - TOT_cases)
dif_15plus <- mutate(c_15plus, "TOT_dif" = TOT_est - TOT_cases)
dif_all <- merge(dif_15plus, dif_014, by = c("country", "iso3"), all.x = TRUE)
FINAL_2019 <- mutate(dif_all, "F_est" = F_est.x + F_est.y, "M_est" = M_est.x + M_est.y, "TOT_est" = TOT_est.x + TOT_est.y, "M_cases" = m_cases.x + m_cases.y, "F_cases" = f_cases.x + f_cases.y, "TOT_cases" = TOT_cases.x + TOT_cases.y, "TOT_dif" = TOT_dif.x + TOT_dif.y)
FINAL_2019 <- FINAL_2019[, c(1,2, 17:23)]
 
```

Isolating the high burden country data for 2019 

```{r}
t_04 <- dif_04[dif_04$country %in% c("Angola", "Bangladesh", "Brazil", "China", "Democratic People's Republic of Korea", "Democratic Republic of the Congo", "Ethiopia", "India", "Indonesia", "Kenya", "Mozambique", "Myanmar", "Nigeria", "Pakistan", "Philippines", "Russian Federation", "South Africa", "Thailand", "United Republic of Tanzania", "Viet Nam", "Cambodia", "Central African Republic", "Congo", "Lesotho", "Liberia", "Namibia", "Papua New Guinea", "Sierra Leone", "Zambia", "Zimbabwe"), ]

t_514 <- dif_514[dif_514$country %in% c("Angola", "Bangladesh", "Brazil", "China", "Democratic People's Republic of Korea", "Democratic Republic of the Congo", "Ethiopia", "India", "Indonesia", "Kenya", "Mozambique", "Myanmar", "Nigeria", "Pakistan", "Philippines", "Russian Federation", "South Africa", "Thailand", "United Republic of Tanzania", "Viet Nam", "Cambodia", "Central African Republic", "Congo", "Lesotho", "Liberia", "Namibia", "Papua New Guinea", "Sierra Leone", "Zambia", "Zimbabwe"), ]

t_014 <- dif_014[dif_04$country %in% c("Angola", "Bangladesh", "Brazil", "China", "Democratic People's Republic of Korea", "Democratic Republic of the Congo", "Ethiopia", "India", "Indonesia", "Kenya", "Mozambique", "Myanmar", "Nigeria", "Pakistan", "Philippines", "Russian Federation", "South Africa", "Thailand", "United Republic of Tanzania", "Viet Nam", "Cambodia", "Central African Republic", "Congo", "Lesotho", "Liberia", "Namibia", "Papua New Guinea", "Sierra Leone", "Zambia", "Zimbabwe"), ]

t_15plus <- dif_15plus[dif_04$country %in% c("Angola", "Bangladesh", "Brazil", "China", "Democratic People's Republic of Korea", "Democratic Republic of the Congo", "Ethiopia", "India", "Indonesia", "Kenya", "Mozambique", "Myanmar", "Nigeria", "Pakistan", "Philippines", "Russian Federation", "South Africa", "Thailand", "United Republic of Tanzania", "Viet Nam", "Cambodia", "Central African Republic", "Congo", "Lesotho", "Liberia", "Namibia", "Papua New Guinea", "Sierra Leone", "Zambia", "Zimbabwe"), ]

t_tot <- FINAL_2019[FINAL_2019$country %in% c("Angola", "Bangladesh", "Brazil", "China", "Democratic People's Republic of Korea", "Democratic Republic of the Congo", "Ethiopia", "India", "Indonesia", "Kenya", "Mozambique", "Myanmar", "Nigeria", "Pakistan", "Philippines", "Russian Federation", "South Africa", "Thailand", "United Republic of Tanzania", "Viet Nam", "Cambodia", "Central African Republic", "Congo", "Lesotho", "Liberia", "Namibia", "Papua New Guinea", "Sierra Leone", "Zambia", "Zimbabwe"), ]

##Adding percentage reported as a column
tp_04 <- mutate(t_04, "perc_tot" = 100 * (TOT_cases/TOT_est))
tp_514 <- mutate(t_514, "perc_tot" = 100 * (TOT_cases/TOT_est))
tp_014 <- mutate(t_014, "perc_tot" = 100 * (TOT_cases/TOT_est))
tp_15plus <- mutate(t_15plus, "perc_tot" = 100 * (TOT_cases/TOT_est))
tp_tot <- mutate(t_tot, "perc_tot" = 100 * (TOT_cases/TOT_est))
```

Merging data frames for 2019 and 2020 

```{r}
comparison_04 <- merge(tp_04, topp_04, by = c("country", "iso3"))
comparison_514 <- merge(tp_514, topp_514, by = c("country", "iso3"))
comparison_014 <- merge(tp_014, topp_014, by = c("country", "iso3"))
comparison_15plus <- merge(tp_15plus, topp_15plus, by = c("country", "iso3"))
comparison_ALL <- merge(tp_tot, topp_tot, by = c("country", "iso3"))

#Adding column for change in percentage reporting between 2019 and 2020 
comp_perc_04 <- mutate(comparison_04, "perc_diff" = perc_tot.y - perc_tot.x)
comp_perc_514 <- mutate(comparison_514, "perc_diff" = perc_tot.y - perc_tot.x)
comp_perc_014 <- mutate(comparison_014, "perc_diff" = perc_tot.y - perc_tot.x)
comp_perc_15plus <- mutate(comparison_15plus, "perc_diff" = perc_tot.y - perc_tot.x)
comp_perc_ALL <- mutate(comparison_ALL, "perc_diff" = perc_tot.y - perc_tot.x)

```

Plotting bar graphs

```{r}
comparison_plot <- barplot(comp_perc_ALL$perc_diff ~ comp_perc_ALL$country, col = c("skyblue"), las = 2, cex.names = 1, xlab = NA, ylab = "Change in Percentage Notification", ylim = c(-60, 10))

compare_04 <- barplot(comp_perc_04$perc_diff ~ comp_perc_04$country, col = c("skyblue"), las = 2, cex.names = 1, xlab = NA, ylab = "Change in Percentage Notification", ylim = c(-60, 20), main = "Change in Perc Notification for 0-4 Years")

compare_514 <- barplot(comp_perc_514$perc_diff ~ comp_perc_514$country, col = c("skyblue"), las = 2, cex.names = 1, xlab = NA, ylab = "Change in Percentage Notification", ylim = c(-60, 20),  main = "Change in Perc Notification for 5-14 Years")

compare_014 <- barplot(comp_perc_014$perc_diff ~ comp_perc_014$country, col = c("skyblue"), las = 2, cex.names = 1, xlab = NA, ylab = "Change in Percentage Notification", ylim = c(-60, 20))

compare_15plus <- barplot(comp_perc_15plus$perc_diff ~ comp_perc_15plus$country, col = c("skyblue"), las = 2, cex.names = 1, xlab = NA, ylab = "Change in Percentage Notification", ylim = c(-60, 20), main = "Change in Perc Notification for 15plus Years")
```
```{r}
#Redoing the change in percentage notification for all countries 
all04_2019 <- mutate(dif_04, "perc_tot" = 100 * (TOT_cases/TOT_est))
all04_2020 <- mutate(dif_tot_04, "perc_tot" = 100 * (TOT_cases/TOT_est))

all514_2019 <- mutate(dif_514, "perc_tot" = 100 * (TOT_cases/TOT_est))
all514_2020 <- mutate(dif_tot_514, "perc_tot" = 100 * (TOT_cases/TOT_est))

all15plus_2019 <- mutate(dif_15plus, "perc_tot" = 100 * (TOT_cases/TOT_est))
all15plus_2020 <- mutate(dif_tot_15plus, "perc_tot" = 100 * (TOT_cases/TOT_est))

all_2019 <- mutate(FINAL_2019, "perc_tot" = 100 * (TOT_cases/TOT_est))
all_2020 <- mutate(FINAL_2020, "perc_tot" = 100 * (TOT_cases/TOT_est))


#merging data frame for all countries
allcomp_04 <- merge(all04_2019, all04_2020, by = c("country", "iso3"))
allcomp_514 <- merge(all514_2019, all514_2020, by = c("country", "iso3"))
allcomp_15plus <- merge(all15plus_2019, all15plus_2020, by = c("country", "iso3"))
allcomp <- merge(all_2019, all_2020, by = c("country", "iso3"))

#Adding column for change in percentage reporting between 2019 and 2020 
allperc04 <- mutate(allcomp_04, "perc_diff" = perc_tot.y - perc_tot.x)
allperc514 <- mutate(allcomp_514, "perc_diff" = perc_tot.y - perc_tot.x)
allperc15plus <- mutate(allcomp_15plus, "perc_diff" = perc_tot.y - perc_tot.x)
allperc <- mutate(allcomp, "perc_diff" = perc_tot.y - perc_tot.x)


###PLOTTING FOR ALL COUNTRIES###
allcomp04_plot <- barplot(allperc04$perc_diff ~ allperc04$country, col = c("skyblue"), axisnames = FALSE, xlab = "Country", ylab = "Change in Percentage Notification", ylim = c(-250, 100), main = "Change in Perc Notification for 0-4 Years")

allcomp514_plot <- barplot(allperc514$perc_diff ~ allperc514$country, col = c("skyblue"), axisnames = FALSE, xlab = "Country", ylab = "Change in Percentage Notification", ylim = c(-150, 100), main = "Change in Perc Notification for 5-14 Years")

allcomp15plus_plot <- barplot(allperc15plus$perc_diff ~ allperc15plus$country, col = c("skyblue"), axisnames = FALSE, xlab = "Country", ylab = "Change in Percentage Notification", ylim = c(-100, 150), main = "Change in Perc Notification for 15plus Years")

allcomp_plot <- barplot(allperc$perc_diff ~ allperc$country, col = c("skyblue"), axisnames = FALSE, xlab = "Country", ylab = "Change in Percentage Notification", ylim = c(-100, 150), main = "Change in Perc Notification for All Ages")


```
Adding the combined 30 country columns to the data frame 

```{r}
total_hbc <- comp_perc_ALL[, c(3:19)] %>% na.omit() %>% sapply(FUN = sum) %>% as.data.frame() %>% t()

total_hbc <- cbind(total_hbc, country = "All_HBCs", iso3 = "HBCs")

total_hbc <- total_hbc[, c(18,19, 1:17)]
total_hbc %<>% as.data.frame()
total_hbc %<>% t()
total_hbc %<>% as.data.frame()
total_hbc[, c(3:19)] %<>% as.numeric()


total_hbc$perc_tot.x <- 100 * (total_hbc$TOT_cases.x/total_hbc$TOT_est.x)
total_hbc$perc_tot.y <- 100 * (total_hbc$TOT_cases.y/total_hbc$TOT_est.y)
total_hbc$perc_diff <- total_hbc$perc_tot.y - total_hbc$perc_tot.x

###Combining the total HBC data with the main data frame before producing a new graph 
add_hbc_all <- rbind(comp_perc_ALL, total_hbc)

final_comp_plot <- barplot(add_hbc_all$perc_diff ~ add_hbc_all$country, col = c("skyblue"), las = 2, cex.names = 1, xlab = NA, ylab = "Change in Percentage Notification", ylim = c(-60, 10))

countries <- as.vector(unique(add_hbc_all$country))
countries_new <- countries[! countries %in% "All_HBCs"]

add_hbc_all$iso3 <- factor(add_hbc_all$iso3, levels = c(unique(add_hbc_all$iso3)))

gg_comp_plot <- ggplot(add_hbc_all, aes(x = iso3, y = perc_diff, fill = iso3)) + 
  geom_bar(stat = "identity") + scale_fill_manual(values = c( "HBCs" = "red")) + theme(axis.text.x = element_text(angle = 90)) + theme(legend.title = element_blank()) + xlab("Country") + ylab("Change in Percentage Notifications") + labs(title = "Change in Percentage Notifications for All Ages")


###Graphs including total for 0-4 years 
total_04 <- comp_perc_04[, c(3:19)] %>% na.omit() %>% sapply(FUN = sum) %>% as.data.frame() %>% t()

total_04 <- cbind(total_04, country = "All_HBCs", iso3 = "HBCs")

total_04 <- total_04[, c(18,19, 1:17)]
total_04 %<>% as.data.frame()
total_04 %<>% t()
total_04 %<>% as.data.frame()
total_04[, c(3:19)] %<>% as.numeric()


total_04$perc_tot.x <- 100 * (total_04$TOT_cases.x/total_04$TOT_est.x)
total_04$perc_tot.y <- 100 * (total_04$TOT_cases.y/total_04$TOT_est.y)
total_04$perc_diff <- total_04$perc_tot.y - total_04$perc_tot.x

add_hbc_04 <- rbind(comp_perc_04, total_04)

final_comp_04 <- barplot(add_hbc_04$perc_diff ~ add_hbc_04$country, col = c("skyblue"), las = 2, cex.names = 1, xlab = NA, ylab = "Change in Percentage Notification", ylim = c(-60, 10))

add_hbc_04$iso3 <- factor(add_hbc_04$iso3, levels = c(unique(add_hbc_04$iso3)))

gg_comp_04 <- ggplot(add_hbc_04, aes(x = iso3, y = perc_diff, fill = iso3)) + 
  geom_bar(stat = "identity") + scale_fill_manual(values = c( "HBCs" = "red")) + theme(axis.text.x = element_text(angle = 90)) + theme(legend.title = element_blank()) + xlab("Country") + ylab("Change in Percentage Notifications") + labs(title = "Change in Percentage Notifications for 0-4 years")

###Graphs including total for 5-14 years 
total_514 <- comp_perc_514[, c(3:19)] %>% na.omit() %>% sapply(FUN = sum) %>% as.data.frame() %>% t()

total_514 <- cbind(total_514, country = "All_HBCs", iso3 = "HBCs")

total_514 <- total_514[, c(18,19, 1:17)]
total_514 %<>% as.data.frame()
total_514 %<>% t()
total_514 %<>% as.data.frame()
total_514[, c(3:19)] %<>% as.numeric()


total_514$perc_tot.x <- 100 * (total_514$TOT_cases.x/total_514$TOT_est.x)
total_514$perc_tot.y <- 100 * (total_514$TOT_cases.y/total_514$TOT_est.y)
total_514$perc_diff <- total_514$perc_tot.y - total_514$perc_tot.x

add_hbc_514 <- rbind(comp_perc_514, total_514)

final_comp_514 <- barplot(add_hbc_514$perc_diff ~ add_hbc_514$country, col = c("skyblue"), las = 2, cex.names = 1, xlab = NA, ylab = "Change in Percentage Notification", ylim = c(-60, 10))

add_hbc_514$iso3 <- factor(add_hbc_514$iso3, levels = c(unique(add_hbc_514$iso3)))

gg_comp_514 <- ggplot(add_hbc_514, aes(x = iso3, y = perc_diff, fill = iso3)) + 
  geom_bar(stat = "identity") + scale_fill_manual(values = c( "HBCs" = "red")) + theme(axis.text.x = element_text(angle = 90)) + theme(legend.title = element_blank()) + xlab("Country") + ylab("Change in Percentage Notifications") + labs(title = "Change in Percentage Notifications for 5-14 years")

###Graphs including total for 15 plus years
total_15plus <- comp_perc_15plus[, c(3:19)] %>% na.omit() %>% sapply(FUN = sum) %>% as.data.frame() %>% t()

total_15plus <- cbind(total_15plus, country = "All_HBCs", iso3 = "HBCs")

total_15plus <- total_15plus[, c(18,19, 1:17)]
total_15plus %<>% as.data.frame()
total_15plus %<>% t()
total_15plus %<>% as.data.frame()
total_15plus[, c(3:19)] %<>% as.numeric()


total_15plus$perc_tot.x <- 100 * (total_15plus$TOT_cases.x/total_15plus$TOT_est.x)
total_15plus$perc_tot.y <- 100 * (total_15plus$TOT_cases.y/total_15plus$TOT_est.y)
total_15plus$perc_diff <- total_15plus$perc_tot.y - total_15plus$perc_tot.x

add_hbc_15plus <- rbind(comp_perc_15plus, total_15plus)

final_comp_15plus <- barplot(add_hbc_15plus$perc_diff ~ add_hbc_15plus$country, col = c("skyblue"), las = 2, cex.names = 1, xlab = NA, ylab = "Change in Percentage Notification", ylim = c(-60, 10))

add_hbc_15plus$iso3 <- factor(add_hbc_15plus$iso3, levels = c(unique(add_hbc_15plus$iso3)))

gg_comp_15plus <- ggplot(add_hbc_15plus, aes(x = iso3, y = perc_diff, fill = iso3)) + 
  geom_bar(stat = "identity") + scale_fill_manual(values = c( "HBCs" = "red")) + theme(axis.text.x = element_text(angle = 90)) + theme(legend.title = element_blank()) + xlab("Country") + ylab("Change in Percentage Notifications") + labs(title = "Change in Percentage Notifications for 15 plus years")


```




