---
title: "Attempt at creating violin plots for 30 high burden countries for 2019 and 2020"
output: html_notebook
---

AIM: To create violin plots that compare the actual notified cases vs the expected cases in each age group in the 30 high burden countries 

Loading the libraries and the data for 2019 
```{r}
library(tidyverse)
library(dplyr)
library(magrittr)
setwd("~/Desktop/AFP/Original Data")
estimate_2019 <- read_csv("TBburden.csv")
cases_2019 <- read_csv("TBnotif.csv")

estimate_2019 %<>% filter(risk_factor == "all")
estimate_2019 %<>% filter(sex != "a")
estimate_2019 <- estimate_2019[, c(1,3,8,9,11,12,13)]

high_estimate <- estimate_2019[estimate_2019$country %in% c("Angola", "Bangladesh", "Brazil", "China", "Democratic People's Republic of Korea", "Democratic Republic of the Congo", "Ethiopia", "India", "Indonesia", "Kenya", "Mozambique", "Myanmar", "Nigeria", "Pakistan", "Philippines", "Russian Federation", "South Africa", "Thailand", "United Republic of Tanzania", "Viet Nam", "Cambodia", "Central African Republic", "Congo", "Lesotho", "Liberia", "Namibia", "Papua New Guinea", "Sierra Leone", "Zambia", "Zimbabwe"), ]

est19_04 <- filter(high_estimate, age_group == "0-4")
est19_514 <- filter(high_estimate, age_group == "5-14")
est19_014 <- filter(high_estimate, age_group == "0-14")
est19_15plus <- filter(high_estimate, age_group == "15plus")

piv19_04 <- pivot_wider(est19_04, names_from = "sex", values_from = c("best", "lo", "hi"))
piv19_04 <- piv19_04[, c(1,2, 5, 7, 9, 4, 6, 8)]

piv19_514 <- pivot_wider(est19_514, names_from = "sex", values_from = c("best", "lo", "hi"))
piv19_514 <- piv19_514[, c(1,2, 5, 7, 9, 4, 6, 8)]

piv19_014 <- pivot_wider(est19_014, names_from = "sex", values_from = c("best", "lo", "hi"))
piv19_014 <- piv19_014[, c(1,2, 5, 7, 9, 4, 6, 8)]

piv19_15plus <- pivot_wider(est19_15plus, names_from = "sex", values_from = c("best", "lo", "hi"))
piv19_15plus <- piv19_15plus[, c(1,2, 5, 7, 9, 4, 6, 8)]


```

Sorting the notificaiton data for 2019 

```{r}
cases_2019 %<>% filter(year == 2019)
casefilter_2019 <- cases_2019[, c(1,3,5, 100, 103, 104, 113, 115, 118, 119, 128)]

high_case2019 <- casefilter_2019[casefilter_2019$country %in% c("Angola", "Bangladesh", "Brazil", "China", "Democratic People's Republic of Korea", "Democratic Republic of the Congo", "Ethiopia", "India", "Indonesia", "Kenya", "Mozambique", "Myanmar", "Nigeria", "Pakistan", "Philippines", "Russian Federation", "South Africa", "Thailand", "United Republic of Tanzania", "Viet Nam", "Cambodia", "Central African Republic", "Congo", "Lesotho", "Liberia", "Namibia", "Papua New Guinea", "Sierra Leone", "Zambia", "Zimbabwe"), ]


```

Combining each data frame 

```{r}
violin19_04 <- cbind(piv19_04, high_case2019$newrel_m04, high_case2019$newrel_f04)
colnames(violin19_04)[colnames(violin19_04) == "high_case2019$newrel_m04"] <- "notif_m04"
colnames(violin19_04)[colnames(violin19_04) == "high_case2019$newrel_f04"] <- "notif_f04"

violin19_514 <- cbind(piv19_514, high_case2019$newrel_m514, high_case2019$newrel_f514)
colnames(violin19_514)[colnames(violin19_514) == "high_case2019$newrel_m514"] <- "notif_m514"
colnames(violin19_514)[colnames(violin19_514) == "high_case2019$newrel_f514"] <- "notif_f514"

violin19_014 <- cbind(piv19_014, high_case2019$newrel_m014, high_case2019$newrel_f014)
colnames(violin19_014)[colnames(violin19_014) == "high_case2019$newrel_m014"] <- "notif_m014"
colnames(violin19_014)[colnames(violin19_014) == "high_case2019$newrel_f014"] <- "notif_f014"


violin19_15plus <- cbind(piv19_15plus, high_case2019$newrel_m15plus, high_case2019$newrel_f15plus)
colnames(violin19_15plus)[colnames(violin19_15plus) == "high_case2019$newrel_m15plus"] <- "notif_m15plus"
colnames(violin19_15plus)[colnames(violin19_15plus) == "high_case2019$newrel_f15plus"] <- "notif_f15plus"

```

Creating boxplots 

```{r}
sub_m04 <- violin19_04[, c(1, 3, 4, 5)]
subpiv_m04 <- pivot_longer(sub_m04, cols = c("best_m", "lo_m", "hi_m"), names_to = "est_m04")
subpiv_m04 <- subpiv_m04[, c(1,3)]
subnot_m04 <- violin19_04[, c(1,9)]
list_m04 <- as.vector(violin19_04$notif_m04)

box_m04 <- boxplot(value ~ country, subpiv_m04, ylab = NULL, horizontal = TRUE, las = 1, cex.names = 0.3, par(mar = c(1, 11, 2, 2)))
points(x = list_m04,
       y = 1:30,
       col = "red",
       pch = 16,)

```

Creating boxplots and excluding Indonesia and India for 0-4 years 

```{r}
iisub_m04 <- violin19_04[, c(1, 3, 4, 5)]
iisub_m04 %<>% filter(country != c("India", "Indonesia"))
iisubpiv_m04 <- pivot_longer(iisub_m04, cols = c("best_m", "lo_m", "hi_m"), names_to = "est_m04")
iisubpiv_m04 <- iisubpiv_m04[, c(1,3)]
iisubnot_m04 <- violin19_04[, c(1,9)]
iisubnot_m04 %<>% filter(country != c("India", "Indonesia"))

box_m04 <- boxplot(value ~ country, iisubpiv_m04, horizontal = TRUE, las = 1, cex.names = 0.1)
points(x = iisubnot_m04$notif_m04,
       y = 1:28,
       col = "red",
       pch = 16)

iisub_f04 <- violin19_04[, c(1, 6:8)]
iisub_f04 %<>% filter(country != c("India", "Indonesia"))
iisubpiv_f04 <- pivot_longer(iisub_f04, cols = c("best_f", "lo_f", "hi_f"), names_to = "est_f04")
iisubpiv_f04 <- iisubpiv_f04[, c(1,3)]
iisubnot_f04 <- violin19_04[, c(1,10)]
iisubnot_f04 %<>% filter(country != c("India", "Indonesia"))

box_f04 <- boxplot(value ~ country, iisubpiv_f04, horizontal = TRUE, las = 1, cex.names = 0.1)
points(x = iisubnot_f04$notif_f04,
       y = 1:28,
       col = "red",
       pch = 16)


```
Creating box plots excluding India and Indonesia for 0-14 years 

```{r}
iisub_m014 <- violin19_014[, c(1, 3, 4, 5)]
iisub_m014 %<>% filter(country != c("India", "Indonesia"))
iisubpiv_m014 <- pivot_longer(iisub_m014, cols = c("best_m", "lo_m", "hi_m"), names_to = "est_m014")
iisubpiv_m014 <- iisubpiv_m014[, c(1,3)]
iisubnot_m014 <- violin19_014[, c(1,9)]
iisubnot_m014 %<>% filter(country != c("India", "Indonesia"))

box_m014 <- boxplot(value ~ country, iisubpiv_m014, horizontal = TRUE, las = 1, cex.names = 0.5)
points(x = iisubnot_m014$notif_m014,
       y = 1:28,
       col = "red",
       pch = 16)

iisub_f014 <- violin19_014[, c(1, 6:8)]
iisub_f014 %<>% filter(country != c("India", "Indonesia"))
iisubpiv_f014 <- pivot_longer(iisub_f014, cols = c("best_f", "lo_f", "hi_f"), names_to = "est_f014")
iisubpiv_f014 <- iisubpiv_f014[, c(1,3)]
iisubnot_f014 <- violin19_014[, c(1,10)]
iisubnot_f014 %<>% filter(country != c("India", "Indonesia"))

box_f014 <- boxplot(value ~ country, iisubpiv_f014, horizontal = TRUE, las = 1, cex.names = 0.5)
points(x = iisubnot_f014$notif_f014,
       y = 1:28,
       col = "red",
       pch = 16)
```
Creating box plots for 15plus years 

```{r}
iisub_m15plus <- violin19_15plus[, c(1, 3, 4, 5)]
iisub_m15plus %<>% filter(country != c("India", "Indonesia"))
iisubpiv_m15plus <- pivot_longer(iisub_m15plus, cols = c("best_m", "lo_m", "hi_m"), names_to = "est_m15plus")
iisubpiv_m15plus <- iisubpiv_m15plus[, c(1,3)]
iisubnot_m15plus <- violin19_15plus[, c(1,9)]
iisubnot_m15plus %<>% filter(country != c("India", "Indonesia"))

box_m15plus <- boxplot(value ~ country, iisubpiv_m15plus, horizontal = TRUE, las = 1, cex.names = 0.5)
points(x = iisubnot_m15plus$notif_m15plus,
       y = 1:28,
       col = "red",
       pch = 16)

iisub_f15plus <- violin19_15plus[, c(1, 6:8)]
iisub_f15plus %<>% filter(country != c("India", "Indonesia"))
iisubpiv_f15plus <- pivot_longer(iisub_f15plus, cols = c("best_f", "lo_f", "hi_f"), names_to = "est_f04")
iisubpiv_f15plus <- iisubpiv_f15plus[, c(1,3)]
iisubnot_f15plus <- violin19_15plus[, c(1,10)]
iisubnot_f15plus %<>% filter(country != c("India", "Indonesia"))

box_f15plus <- boxplot(value ~ country, iisubpiv_f15plus, horizontal = TRUE, las = 1, cex.names = 0.5)
points(x = iisubnot_f15plus$notif_f15plus,
       y = 1:28,
       col = "red",
       pch = 16)

```


Repeating same data analysis for 2020

```{r}
setwd("~/Desktop/AFP/modV3/data")
burden_2020 <- read_csv("TB_burden_2020.csv")
notif_2020 <- read_csv("TB_notifications.csv")

burden_clean <- filter(burden_2020, risk_factor == "all")
burden_clean %<>% filter(sex != "a")
burden20_04 <- filter(burden_clean, age_group == "0-4")
burden20_514 <- filter(burden_clean, age_group == "5-14")
burden20_014 <- filter(burden_clean, age_group == "0-14")
burden20_15plus <- filter(burden_clean, age_group == "15plus")

burden20_04 <- burden20_04[, c(1,3,9,11,12,13)]
burden20_514 <- burden20_514[, c(1,3,9,11,12,13)]
burden20_014 <- burden20_014[, c(1,3,9,11,12,13)]
burden20_15plus <- burden20_15plus[, c(1,3,9,11,12,13)]

male20_04 <- filter(burden20_04, sex == "m")
female20_04 <- filter(burden20_04, sex == "f")
male20_514 <- filter(burden20_514, sex == "m")
female20_514 <- filter(burden20_514, sex == "f")
male20_014 <- filter(burden20_014, sex == "m")
female20_014 <- filter(burden20_014, sex == "f")
male20_15plus <- filter(burden20_15plus, sex == "m")
female20_15plus <- filter(burden20_15plus, sex == "f")

#Pivoted tables of estimates for creation of bar plots 
pivmale_04 <- pivot_longer(male20_04, cols = c("best", "lo", "hi"), names_to = "est")
pivmale_04 <- pivmale_04[, c(1,4)]
pivfemale_04 <- pivot_longer(female20_04, cols = c("best", "lo", "hi"), names_to = "est")
pivfemale_04 <- pivfemale_04[, c(1,4)]
pivmale_514 <- pivot_longer(male20_514, cols = c("best", "lo", "hi"), names_to = "est")
pivmale_514 <- pivmale_514[, c(1,4)]
pivfemale_514 <- pivot_longer(female20_514, cols = c("best", "lo", "hi"), names_to = "est")
pivfemale_514 <- pivfemale_514[, c(1,4)]
pivmale_014 <- pivot_longer(male20_014, cols = c("best", "lo", "hi"), names_to = "est")
pivmale_014 <- pivmale_014[, c(1,4)]
pivfemale_014 <- pivot_longer(female20_014, cols = c("best", "lo", "hi"), names_to = "est")
pivfemale_014 <- pivfemale_014[, c(1,4)]
pivmale_15plus <- pivot_longer(male20_15plus, cols = c("best", "lo", "hi"), names_to = "est")
pivmale_15plus <- pivmale_15plus[, c(1,4)]
pivfemale_15plus <- pivot_longer(female20_15plus, cols = c("best", "lo", "hi"), names_to = "est")
pivfemale_15plus <- pivfemale_15plus[, c(1,4)]

#Extracting the notification data for 2020 to add to the bar plot 
notif_2020 %<>% filter(year == 2020)
comboM20_04 <- merge(male20_04, notif_2020[, c(3, 100)], by = "iso3")
comboM20_514 <- merge(male20_514, notif_2020[, c(3, 103)], by = "iso3")
comboM20_014 <- merge(male20_014, notif_2020[, c(3, 104)], by = "iso3")
comboM20_15plus <- merge(male20_15plus, notif_2020[, c(3, 113)], by = "iso3")

comboF20_04 <- merge(female20_04, notif_2020[, c(3, 115)], by = "iso3")
comboF20_514 <- merge(female20_514, notif_2020[, c(3, 118)], by = "iso3")
comboF20_014 <- merge(female20_014, notif_2020[, c(3, 119)], by = "iso3")
comboF20_15plus <- merge(female20_15plus, notif_2020[, c(3, 128)], by = "iso3")

```
Isolating the data for high burden countries excluding India and Indonesia
```{r}
ii_2020_m04 <-  comboM20_04[comboM20_04$country %in% c("Angola", "Bangladesh", "Brazil", "China", "Democratic People's Republic of Korea", "Democratic Republic of the Congo", "Ethiopia", "Kenya", "Mozambique", "Myanmar", "Nigeria", "Pakistan", "Philippines", "Russian Federation", "South Africa", "Thailand", "United Republic of Tanzania", "Viet Nam", "Cambodia", "Central African Republic", "Congo", "Lesotho", "Liberia", "Namibia", "Papua New Guinea", "Sierra Leone", "Zambia", "Zimbabwe"), ]

ii_2020_f04 <-  comboF20_04[comboF20_04$country %in% c("Angola", "Bangladesh", "Brazil", "China", "Democratic People's Republic of Korea", "Democratic Republic of the Congo", "Ethiopia", "Kenya", "Mozambique", "Myanmar", "Nigeria", "Pakistan", "Philippines", "Russian Federation", "South Africa", "Thailand", "United Republic of Tanzania", "Viet Nam", "Cambodia", "Central African Republic", "Congo", "Lesotho", "Liberia", "Namibia", "Papua New Guinea", "Sierra Leone", "Zambia", "Zimbabwe"), ]

ii_2020_m514 <-  comboM20_514[comboM20_514$country %in% c("Angola", "Bangladesh", "Brazil", "China", "Democratic People's Republic of Korea", "Democratic Republic of the Congo", "Ethiopia", "Kenya", "Mozambique", "Myanmar", "Nigeria", "Pakistan", "Philippines", "Russian Federation", "South Africa", "Thailand", "United Republic of Tanzania", "Viet Nam", "Cambodia", "Central African Republic", "Congo", "Lesotho", "Liberia", "Namibia", "Papua New Guinea", "Sierra Leone", "Zambia", "Zimbabwe"), ]

ii_2020_f514 <-  comboF20_514[comboF20_514$country %in% c("Angola", "Bangladesh", "Brazil", "China", "Democratic People's Republic of Korea", "Democratic Republic of the Congo", "Ethiopia", "Kenya", "Mozambique", "Myanmar", "Nigeria", "Pakistan", "Philippines", "Russian Federation", "South Africa", "Thailand", "United Republic of Tanzania", "Viet Nam", "Cambodia", "Central African Republic", "Congo", "Lesotho", "Liberia", "Namibia", "Papua New Guinea", "Sierra Leone", "Zambia", "Zimbabwe"), ]

ii_2020_m014 <-  comboM20_014[comboM20_014$country %in% c("Angola", "Bangladesh", "Brazil", "China", "Democratic People's Republic of Korea", "Democratic Republic of the Congo", "Ethiopia", "Kenya", "Mozambique", "Myanmar", "Nigeria", "Pakistan", "Philippines", "Russian Federation", "South Africa", "Thailand", "United Republic of Tanzania", "Viet Nam", "Cambodia", "Central African Republic", "Congo", "Lesotho", "Liberia", "Namibia", "Papua New Guinea", "Sierra Leone", "Zambia", "Zimbabwe"), ]

ii_2020_f014 <-  comboF20_014[comboF20_014$country %in% c("Angola", "Bangladesh", "Brazil", "China", "Democratic People's Republic of Korea", "Democratic Republic of the Congo", "Ethiopia", "Kenya", "Mozambique", "Myanmar", "Nigeria", "Pakistan", "Philippines", "Russian Federation", "South Africa", "Thailand", "United Republic of Tanzania", "Viet Nam", "Cambodia", "Central African Republic", "Congo", "Lesotho", "Liberia", "Namibia", "Papua New Guinea", "Sierra Leone", "Zambia", "Zimbabwe"), ]

ii_2020_m15plus <-  comboM20_15plus[comboM20_15plus$country %in% c("Angola", "Bangladesh", "Brazil", "China", "Democratic People's Republic of Korea", "Democratic Republic of the Congo", "Ethiopia", "Kenya", "Mozambique", "Myanmar", "Nigeria", "Pakistan", "Philippines", "Russian Federation", "South Africa", "Thailand", "United Republic of Tanzania", "Viet Nam", "Cambodia", "Central African Republic", "Congo", "Lesotho", "Liberia", "Namibia", "Papua New Guinea", "Sierra Leone", "Zambia", "Zimbabwe"), ]

ii_2020_f15plus <-  comboF20_15plus[comboF20_15plus$country %in% c("Angola", "Bangladesh", "Brazil", "China", "Democratic People's Republic of Korea", "Democratic Republic of the Congo", "Ethiopia", "Kenya", "Mozambique", "Myanmar", "Nigeria", "Pakistan", "Philippines", "Russian Federation", "South Africa", "Thailand", "United Republic of Tanzania", "Viet Nam", "Cambodia", "Central African Republic", "Congo", "Lesotho", "Liberia", "Namibia", "Papua New Guinea", "Sierra Leone", "Zambia", "Zimbabwe"), ]


```

Prepping data for box plots 

```{r}
topiv_m04 <- ii_2020_m04[, c(2,4:6)]
pivved_m04 <- pivot_longer(topiv_m04, cols = c("best", "lo", "hi"), names_to = "est")
pivved_m04 <- pivved_m04[, c(1,3)]

topiv_f04 <- ii_2020_f04[, c(2,4:6)]
pivved_f04 <- pivot_longer(topiv_f04, cols = c("best", "lo", "hi"), names_to = "est")
pivved_f04 <- pivved_f04[, c(1,3)]

topiv_m514 <- ii_2020_m514[, c(2,4:6)]
pivved_m514 <- pivot_longer(topiv_m514, cols = c("best", "lo", "hi"), names_to = "est")
pivved_m514 <- pivved_m514[, c(1,3)]

topiv_f514 <- ii_2020_f514[, c(2,4:6)]
pivved_f514 <- pivot_longer(topiv_f514, cols = c("best", "lo", "hi"), names_to = "est")
pivved_f514 <- pivved_f514[, c(1,3)]

topiv_m014 <- ii_2020_m014[, c(2,4:6)]
pivved_m014 <- pivot_longer(topiv_m014, cols = c("best", "lo", "hi"), names_to = "est")
pivved_m014 <- pivved_m014[, c(1,3)]

topiv_f014 <- ii_2020_f014[, c(2,4:6)]
pivved_f014 <- pivot_longer(topiv_f014, cols = c("best", "lo", "hi"), names_to = "est")
pivved_f014 <- pivved_f014[, c(1,3)]


topiv_m15plus <- ii_2020_m15plus[, c(2,4:6)]
pivved_m15plus <- pivot_longer(topiv_m15plus, cols = c("best", "lo", "hi"), names_to = "est")
pivved_m15plus <- pivved_m15plus[, c(1,3)]


topiv_f15plus <- ii_2020_f15plus[, c(2,4:6)]
pivved_f15plus <- pivot_longer(topiv_f15plus, cols = c("best", "lo", "hi"), names_to = "est")
pivved_f15plus <- pivved_f15plus[, c(1,3)]


```

Creating box plots for high burden countries excluding 
```{r}
box20_m04 <- boxplot(value ~ country, pivved_m04, horizontal = TRUE, las = 1, cex.names = 0.5)
ii_2020_m04 <- ii_2020_m04[order(ii_2020_m04$country), ]
points(x = ii_2020_m04$newrel_m04,
       y = 1:28,
       col = "red",
       pch = 16)

box20_f04 <- boxplot(value ~ country, pivved_f04, horizontal = TRUE, las = 1, cex.names = 0.5)
ii_2020_f04 <- ii_2020_f04[order(ii_2020_f04$country), ]
points(x = ii_2020_f04$newrel_f04,
       y = 1:28,
       col = "red",
       pch = 16)

box20_m514 <- boxplot(value ~ country, pivved_m514, horizontal = TRUE, las = 1, cex.names = 0.5)
ii_2020_m514 <- ii_2020_m514[order(ii_2020_m514$country), ]
points(x = ii_2020_m514$newrel_m514,
       y = 1:28,
       col = "red",
       pch = 16)

box20_f514 <- boxplot(value ~ country, pivved_f514, horizontal = TRUE, las = 1, cex.names = 0.5)
ii_2020_f514 <- ii_2020_f514[order(ii_2020_f514$country), ]
points(x = ii_2020_f514$newrel_f514,
       y = 1:28,
       col = "red",
       pch = 16)

box20_m014 <- boxplot(value ~ country, pivved_m014, horizontal = TRUE, las = 1, cex.names = 0.5)
ii_2020_m014 <- ii_2020_m014[order(ii_2020_m014$country), ]
points(x = ii_2020_m014$newrel_m014,
       y = 1:28,
       col = "red",
       pch = 16)

box20_f014 <- boxplot(value ~ country, pivved_f014, horizontal = TRUE, las = 1, cex.names = 0.5)
ii_2020_f014 <- ii_2020_f014[order(ii_2020_f014$country), ]
points(x = ii_2020_f014$newrel_f014,
       y = 1:28,
       col = "red",
       pch = 16)

box20_m15plus <- boxplot(value ~ country, pivved_m15plus, horizontal = TRUE, las = 1, cex.names = 0.5)
ii_2020_m15plus <- ii_2020_m15plus[order(ii_2020_m15plus$country), ]
points(x = ii_2020_m15plus$newrel_m15plus,
       y = 1:28,
       col = "red",
       pch = 16)

box20_f15plus <- boxplot(value ~ country, pivved_f15plus, horizontal = TRUE, las = 1, cex.names = 0.5)
ii_2020_f15plus <- ii_2020_f15plus[order(ii_2020_f15plus$country), ]
points(x = ii_2020_f15plus$newrel_f15plus,
       y = 1:28,
       col = "red",
       pch = 16)

```

Performing same analysis by continent starting with 2019 data 

```{r}
est19_04 <- filter(estimate_2019, age_group == "0-4")
est19_514 <- filter(estimate_2019, age_group == "5-14")
est19_014 <- filter(estimate_2019, age_group == "0-14")
est19_15plus <- filter(estimate_2019, age_group == "15plus")

estM19_04 <- filter(est19_04, sex == "m")
estF19_04 <- filter(est19_04, sex == "f")
estM19_514 <- filter(est19_514, sex == "m")
estF19_514 <- filter(est19_514, sex == "f")
estM19_014 <- filter(est19_014, sex == "m")
estF19_014 <- filter(est19_014, sex == "f")
estM19_15plus <- filter(est19_15plus, sex == "m")
estF19_15plus <- filter(est19_15plus, sex == "f")

estM19_04 <- estM19_04[, -c(3,4)]
estF19_04 <- estF19_04[, -c(3,4)]
estM19_514 <- estM19_514[, -c(3,4)]
estF19_514 <- estF19_514[, -c(3,4)]
estM19_014 <- estM19_014[, -c(3,4)]
estF19_014 <- estF19_014[, -c(3,4)]
estM19_15plus <- estM19_15plus[, -c(3,4)]
estF19_15plus <- estF19_15plus[, -c(3,4)]

###Adding in the case notification data for 2019
tot_19_m04 <- merge(estM19_04, casefilter_2019[,c(1:4)], by = c("country", "iso3"))
tot_19_m04 <- tot_19_m04[,c(1,2,6,3:5, 7)]
colnames(tot_19_m04)[colnames(tot_19_m04) == "newrel_m04"] <- "cases"

tot_19_f04 <- merge(estF19_04, casefilter_2019[,c(1:3, 8)], by = c("country", "iso3"))
tot_19_f04 <- tot_19_f04[,c(1,2,6,3:5, 7)]
colnames(tot_19_f04)[colnames(tot_19_f04) == "newrel_f04"] <- "cases"

tot_19_m514 <- merge(estM19_514, casefilter_2019[,c(1:3, 5)], by = c("country", "iso3"))
tot_19_m514 <- tot_19_m514[,c(1,2,6,3:5, 7)]
colnames(tot_19_m514)[colnames(tot_19_m514) == "newrel_m514"] <- "cases"

tot_19_f514 <- merge(estF19_514, casefilter_2019[,c(1:3, 9)], by = c("country", "iso3"))
tot_19_f514 <- tot_19_f514[,c(1,2,6,3:5, 7)]
colnames(tot_19_f514)[colnames(tot_19_f514) == "newrel_f514"] <- "cases"

tot_19_m014 <- merge(estM19_014, casefilter_2019[,c(1:3, 6)], by = c("country", "iso3"))
tot_19_m014 <- tot_19_m014[,c(1,2,6,3:5, 7)]
colnames(tot_19_m014)[colnames(tot_19_m014) == "newrel_m014"] <- "cases"

tot_19_f014 <- merge(estF19_014, casefilter_2019[,c(1:3, 10)], by = c("country", "iso3"))
tot_19_f014 <- tot_19_f014[,c(1,2,6,3:5, 7)]
colnames(tot_19_f014)[colnames(tot_19_f014) == "newrel_f014"] <- "cases"

tot_19_m15plus <- merge(estM19_15plus, casefilter_2019[,c(1:3, 7)], by = c("country", "iso3"))
tot_19_m15plus <- tot_19_m15plus[,c(1,2,6,3:5, 7)]
colnames(tot_19_m15plus)[colnames(tot_19_m15plus) == "newrel_m15plus"] <- "cases"

tot_19_f15plus <- merge(estF19_15plus, casefilter_2019[,c(1:3, 11)], by = c("country", "iso3"))
tot_19_f15plus <- tot_19_f15plus[,c(1,2,6,3:5, 7)]
colnames(tot_19_f15plus)[colnames(tot_19_f15plus) == "newrel_f15plus"] <- "cases"


##Extracting information percontinent 
sum_best_m04 <- tot_19_m04 %>% group_by(g_whoregion) %>% summarise(total = sum(best))
sum_lo_m04 <- tot_19_m04 %>% group_by(g_whoregion) %>% summarise(total = sum(lo))
sum_hi_m04 <- tot_19_m04 %>% group_by(g_whoregion) %>% summarise(total = sum(hi))
sum_cases_m04 <- tot_19_m04 %>% group_by(g_whoregion) %>% summarise(total = sum(na.omit(cases)))
merge19_m04 <- cbind(sum_best_m04, sum_lo_m04$total, sum_hi_m04$total, sum_cases_m04$total)
colnames(merge19_m04) <- c("g_whoregion", "best", "lo", "hi", "cases")

sum_best_f04 <- tot_19_f04 %>% group_by(g_whoregion) %>% summarise(total = sum(best))
sum_lo_f04 <- tot_19_f04 %>% group_by(g_whoregion) %>% summarise(total = sum(lo))
sum_hi_f04 <- tot_19_f04 %>% group_by(g_whoregion) %>% summarise(total = sum(hi))
sum_cases_f04 <- tot_19_f04 %>% group_by(g_whoregion) %>% summarise(total = sum(na.omit(cases)))
merge19_f04 <- cbind(sum_best_f04, sum_lo_f04$total, sum_hi_f04$total, sum_cases_f04$total)
colnames(merge19_f04) <- c("g_whoregion", "best", "lo", "hi", "cases")

sum_best_m014 <- tot_19_m014 %>% group_by(g_whoregion) %>% summarise(total = sum(best))
sum_lo_m014 <- tot_19_m014 %>% group_by(g_whoregion) %>% summarise(total = sum(lo))
sum_hi_m014 <- tot_19_m014 %>% group_by(g_whoregion) %>% summarise(total = sum(hi))
sum_cases_m014 <- tot_19_m014 %>% group_by(g_whoregion) %>% summarise(total = sum(na.omit(cases)))
merge19_m014 <- cbind(sum_best_m014, sum_lo_m014$total, sum_hi_m014$total, sum_cases_m014$total)
colnames(merge19_m014) <- c("g_whoregion", "best", "lo", "hi", "cases")

sum_best_f014 <- tot_19_f014 %>% group_by(g_whoregion) %>% summarise(total = sum(best))
sum_lo_f014 <- tot_19_f014 %>% group_by(g_whoregion) %>% summarise(total = sum(lo))
sum_hi_f014 <- tot_19_f014 %>% group_by(g_whoregion) %>% summarise(total = sum(hi))
sum_cases_f014 <- tot_19_f014 %>% group_by(g_whoregion) %>% summarise(total = sum(na.omit(cases)))
merge19_f014 <- cbind(sum_best_f014, sum_lo_f014$total, sum_hi_f014$total, sum_cases_f014$total)
colnames(merge19_f014) <- c("g_whoregion", "best", "lo", "hi", "cases")

sum_best_m514 <- tot_19_m514 %>% group_by(g_whoregion) %>% summarise(total = sum(best))
sum_lo_m514 <- tot_19_m514 %>% group_by(g_whoregion) %>% summarise(total = sum(lo))
sum_hi_m514 <- tot_19_m514 %>% group_by(g_whoregion) %>% summarise(total = sum(hi))
sum_cases_m514 <- tot_19_m514 %>% group_by(g_whoregion) %>% summarise(total = sum(na.omit(cases)))
merge19_m514 <- cbind(sum_best_m514, sum_lo_m514$total, sum_hi_m514$total, sum_cases_m514$total)
colnames(merge19_m514) <- c("g_whoregion", "best", "lo", "hi", "cases")

sum_best_f514 <- tot_19_f514 %>% group_by(g_whoregion) %>% summarise(total = sum(best))
sum_lo_f514 <- tot_19_f514 %>% group_by(g_whoregion) %>% summarise(total = sum(lo))
sum_hi_f514 <- tot_19_f514 %>% group_by(g_whoregion) %>% summarise(total = sum(hi))
sum_cases_f514 <- tot_19_f514 %>% group_by(g_whoregion) %>% summarise(total = sum(na.omit(cases)))
merge19_f514 <- cbind(sum_best_f514, sum_lo_f514$total, sum_hi_f514$total, sum_cases_f514$total)
colnames(merge19_f514) <- c("g_whoregion", "best", "lo", "hi", "cases")

sum_best_m15plus <- tot_19_m15plus %>% group_by(g_whoregion) %>% summarise(total = sum(best))
sum_lo_m15plus <- tot_19_m15plus %>% group_by(g_whoregion) %>% summarise(total = sum(lo))
sum_hi_m15plus <- tot_19_m15plus %>% group_by(g_whoregion) %>% summarise(total = sum(hi))
sum_cases_m15plus <- tot_19_m15plus %>% group_by(g_whoregion) %>% summarise(total = sum(na.omit(cases)))
merge19_m15plus <- cbind(sum_best_m15plus, sum_lo_m15plus$total, sum_hi_m15plus$total, sum_cases_m15plus$total)
colnames(merge19_m15plus) <- c("g_whoregion", "best", "lo", "hi", "cases")

sum_best_f15plus <- tot_19_f15plus %>% group_by(g_whoregion) %>% summarise(total = sum(best))
sum_lo_f15plus <- tot_19_f15plus %>% group_by(g_whoregion) %>% summarise(total = sum(lo))
sum_hi_f15plus <- tot_19_f15plus %>% group_by(g_whoregion) %>% summarise(total = sum(hi))
sum_cases_f15plus <- tot_19_f15plus %>% group_by(g_whoregion) %>% summarise(total = sum(na.omit(cases)))
merge19_f15plus <- cbind(sum_best_f15plus, sum_lo_f15plus$total, sum_hi_f15plus$total, sum_cases_f15plus$total)
colnames(merge19_f15plus) <- c("g_whoregion", "best", "lo", "hi", "cases")

```

Plotting boxplots for continent data for 2019 

```{r}
pivtot_m04 <- pivot_longer(merge19_m04, cols = c("best", "lo", "hi"), names_to = "est")
box19_m04 <- boxplot(value ~ g_whoregion, pivtot_m04, horizontal = TRUE, las = 1, cex.names = 0.5)
points(x = merge19_m04$cases,
       y = 1:6,
       col = "red",
       pch = 16)

pivtot_f04 <- pivot_longer(merge19_f04, cols = c("best", "lo", "hi"), names_to = "est")
box19_f04 <- boxplot(value ~ g_whoregion, pivtot_f04, horizontal = TRUE, las = 1, cex.names = 0.5)
points(x = merge19_f04$cases,
       y = 1:6,
       col = "red",
       pch = 16)

pivtot_m514 <- pivot_longer(merge19_m514, cols = c("best", "lo", "hi"), names_to = "est")
box19_m514 <- boxplot(value ~ g_whoregion, pivtot_m514, horizontal = TRUE, las = 1, cex.names = 0.5)
points(x = merge19_m514$cases,
       y = 1:6,
       col = "red",
       pch = 16)

pivtot_f514 <- pivot_longer(merge19_f514, cols = c("best", "lo", "hi"), names_to = "est")
box19_f514 <- boxplot(value ~ g_whoregion, pivtot_f514, horizontal = TRUE, las = 1, cex.names = 0.5)
points(x = merge19_f514$cases,
       y = 1:6,
       col = "red",
       pch = 16)

pivtot_m014 <- pivot_longer(merge19_m014, cols = c("best", "lo", "hi"), names_to = "est")
box19_m014 <- boxplot(value ~ g_whoregion, pivtot_m014, horizontal = TRUE, las = 1, cex.names = 0.5)
points(x = merge19_m014$cases,
       y = 1:6,
       col = "red",
       pch = 16)

pivtot_f014 <- pivot_longer(merge19_f014, cols = c("best", "lo", "hi"), names_to = "est")
box19_f014 <- boxplot(value ~ g_whoregion, pivtot_f014, horizontal = TRUE, las = 1, cex.names = 0.5)
points(x = merge19_f014$cases,
       y = 1:6,
       col = "red",
       pch = 16)


pivtot_m15plus <- pivot_longer(merge19_m15plus, cols = c("best", "lo", "hi"), names_to = "est")
box19_m15plus <- boxplot(value ~ g_whoregion, pivtot_m15plus, horizontal = TRUE, las = 1, cex.names = 0.5)
points(x = merge19_m15plus$cases,
       y = 1:6,
       col = "red",
       pch = 16)

pivtot_f15plus <- pivot_longer(merge19_f15plus, cols = c("best", "lo", "hi"), names_to = "est")
box19_f15plus <- boxplot(value ~ g_whoregion, pivtot_f15plus, horizontal = TRUE, las = 1, cex.names = 0.5)
points(x = merge19_f15plus$cases,
       y = 1:6,
       col = "red",
       pch = 16)

```
Performing continental analysis with 2020 data 

```{r}
#Adding g_whoregion to the combined data frames
regionM20_04 <- merge(male20_04, notif_2020[, c(3, 5,100)], by = "iso3")
regionM20_514 <- merge(male20_514, notif_2020[, c(3, 5, 103)], by = "iso3")
regionM20_014 <- merge(male20_014, notif_2020[, c(3, 5, 104)], by = "iso3")
regionM20_15plus <- merge(male20_15plus, notif_2020[, c(3, 5, 113)], by = "iso3")

regionF20_04 <- merge(female20_04, notif_2020[, c(3, 5, 115)], by = "iso3")
regionF20_514 <- merge(female20_514, notif_2020[, c(3, 5, 118)], by = "iso3")
regionF20_014 <- merge(female20_014, notif_2020[, c(3, 5, 119)], by = "iso3")
regionF20_15plus <- merge(female20_15plus, notif_2020[, c(3, 5, 128)], by = "iso3")

colnames(regionM20_04)[colnames(regionM20_04) == "newrel_m04"] <- "cases"
colnames(regionM20_514)[colnames(regionM20_514) == "newrel_m514"] <- "cases"
colnames(regionM20_014)[colnames(regionM20_014) == "newrel_m014"] <- "cases"
colnames(regionM20_15plus)[colnames(regionM20_15plus) == "newrel_m15plus"] <- "cases"

colnames(regionF20_04)[colnames(regionF20_04) == "newrel_f04"] <- "cases"
colnames(regionF20_514)[colnames(regionF20_514) == "newrel_f514"] <- "cases"
colnames(regionF20_014)[colnames(regionF20_014) == "newrel_f014"] <- "cases"
colnames(regionF20_15plus)[colnames(regionF20_15plus) == "newrel_f15plus"] <- "cases"

#Creating data for the boxplots 
sum20_best_m04 <- regionM20_04 %>% group_by(g_whoregion) %>% summarise(total = sum(best))
sum20_lo_m04 <- regionM20_04 %>% group_by(g_whoregion) %>% summarise(total = sum(lo))
sum20_hi_m04 <- regionM20_04 %>% group_by(g_whoregion) %>% summarise(total = sum(hi))
sum20_cases_m04 <- regionM20_04 %>% group_by(g_whoregion) %>% summarise(total = sum(na.omit(cases)))
merge20_m04 <- cbind(sum20_best_m04, sum20_lo_m04$total, sum20_hi_m04$total, sum20_cases_m04$total)
colnames(merge20_m04) <- c("g_whoregion", "best", "lo", "hi", "cases")

sum20_best_f04 <- regionF20_04 %>% group_by(g_whoregion) %>% summarise(total = sum(best))
sum20_lo_f04 <- regionF20_04 %>% group_by(g_whoregion) %>% summarise(total = sum(lo))
sum20_hi_f04 <- regionF20_04 %>% group_by(g_whoregion) %>% summarise(total = sum(hi))
sum20_cases_f04 <- regionF20_04 %>% group_by(g_whoregion) %>% summarise(total = sum(na.omit(cases)))
merge20_f04 <- cbind(sum20_best_f04, sum20_lo_f04$total, sum20_hi_f04$total, sum20_cases_f04$total)
colnames(merge20_f04) <- c("g_whoregion", "best", "lo", "hi", "cases")

sum20_best_m514 <- regionM20_514 %>% group_by(g_whoregion) %>% summarise(total = sum(best))
sum20_lo_m514 <- regionM20_514 %>% group_by(g_whoregion) %>% summarise(total = sum(lo))
sum20_hi_m514 <- regionM20_514 %>% group_by(g_whoregion) %>% summarise(total = sum(hi))
sum20_cases_m514 <- regionM20_514 %>% group_by(g_whoregion) %>% summarise(total = sum(na.omit(cases)))
merge20_m514 <- cbind(sum20_best_m514, sum20_lo_m514$total, sum20_hi_m514$total, sum20_cases_m514$total)
colnames(merge20_m514) <- c("g_whoregion", "best", "lo", "hi", "cases")

sum20_best_f514 <- regionF20_514 %>% group_by(g_whoregion) %>% summarise(total = sum(best))
sum20_lo_f514 <- regionF20_514 %>% group_by(g_whoregion) %>% summarise(total = sum(lo))
sum20_hi_f514 <- regionF20_514 %>% group_by(g_whoregion) %>% summarise(total = sum(hi))
sum20_cases_f514 <- regionF20_514 %>% group_by(g_whoregion) %>% summarise(total = sum(na.omit(cases)))
merge20_f514 <- cbind(sum20_best_f514, sum20_lo_f514$total, sum20_hi_f514$total, sum20_cases_f514$total)
colnames(merge20_f514) <- c("g_whoregion", "best", "lo", "hi", "cases")

sum20_best_m014 <- regionM20_014 %>% group_by(g_whoregion) %>% summarise(total = sum(best))
sum20_lo_m014 <- regionM20_014 %>% group_by(g_whoregion) %>% summarise(total = sum(lo))
sum20_hi_m014 <- regionM20_014 %>% group_by(g_whoregion) %>% summarise(total = sum(hi))
sum20_cases_m014 <- regionM20_014 %>% group_by(g_whoregion) %>% summarise(total = sum(na.omit(cases)))
merge20_m014 <- cbind(sum20_best_m014, sum20_lo_m014$total, sum20_hi_m014$total, sum20_cases_m014$total)
colnames(merge20_m014) <- c("g_whoregion", "best", "lo", "hi", "cases")

sum20_best_f014 <- regionF20_014 %>% group_by(g_whoregion) %>% summarise(total = sum(best))
sum20_lo_f014 <- regionF20_014 %>% group_by(g_whoregion) %>% summarise(total = sum(lo))
sum20_hi_f014 <- regionF20_014 %>% group_by(g_whoregion) %>% summarise(total = sum(hi))
sum20_cases_f014 <- regionF20_014 %>% group_by(g_whoregion) %>% summarise(total = sum(na.omit(cases)))
merge20_f014 <- cbind(sum20_best_f014, sum20_lo_f014$total, sum20_hi_f014$total, sum20_cases_f014$total)
colnames(merge20_f014) <- c("g_whoregion", "best", "lo", "hi", "cases")

sum20_best_m15plus <- regionM20_15plus %>% group_by(g_whoregion) %>% summarise(total = sum(best))
sum20_lo_m15plus <- regionM20_15plus %>% group_by(g_whoregion) %>% summarise(total = sum(lo))
sum20_hi_m15plus <- regionM20_15plus %>% group_by(g_whoregion) %>% summarise(total = sum(hi))
sum20_cases_m15plus <- regionM20_15plus %>% group_by(g_whoregion) %>% summarise(total = sum(na.omit(cases)))
merge20_m15plus <- cbind(sum20_best_m15plus, sum20_lo_m15plus$total, sum20_hi_m15plus$total, sum20_cases_m15plus$total)
colnames(merge20_m15plus) <- c("g_whoregion", "best", "lo", "hi", "cases")

sum20_best_f15plus <- regionF20_15plus %>% group_by(g_whoregion) %>% summarise(total = sum(best))
sum20_lo_f15plus <- regionF20_15plus %>% group_by(g_whoregion) %>% summarise(total = sum(lo))
sum20_hi_f15plus <- regionF20_15plus %>% group_by(g_whoregion) %>% summarise(total = sum(hi))
sum20_cases_f15plus <- regionF20_15plus %>% group_by(g_whoregion) %>% summarise(total = sum(na.omit(cases)))
merge20_f15plus <- cbind(sum20_best_f15plus, sum20_lo_f15plus$total, sum20_hi_f15plus$total, sum20_cases_f15plus$total)
colnames(merge20_f15plus) <- c("g_whoregion", "best", "lo", "hi", "cases")


#Drawing box plots for 2020

piv20_m04 <- pivot_longer(merge20_m04, cols = c("best", "lo", "hi"), names_to = "est")
box20_m04 <- boxplot(value ~ g_whoregion, piv20_m04, horizontal = TRUE, las = 1, cex.names = 0.5)
points(x = merge20_m04$cases,
       y = 1:6,
       col = "red",
       pch = 16)

piv20_f04 <- pivot_longer(merge20_f04, cols = c("best", "lo", "hi"), names_to = "est")
box20_f04 <- boxplot(value ~ g_whoregion, piv20_f04, horizontal = TRUE, las = 1, cex.names = 0.5)
points(x = merge20_f04$cases,
       y = 1:6,
       col = "red",
       pch = 16)

piv20_m514 <- pivot_longer(merge20_m514, cols = c("best", "lo", "hi"), names_to = "est")
box20_m514 <- boxplot(value ~ g_whoregion, piv20_m514, horizontal = TRUE, las = 1, cex.names = 0.5)
points(x = merge20_m514$cases,
       y = 1:6,
       col = "red",
       pch = 16)

piv20_f514 <- pivot_longer(merge20_f514, cols = c("best", "lo", "hi"), names_to = "est")
box20_f514 <- boxplot(value ~ g_whoregion, piv20_f514, horizontal = TRUE, las = 1, cex.names = 0.5)
points(x = merge20_f514$cases,
       y = 1:6,
       col = "red",
       pch = 16)

piv20_m014 <- pivot_longer(merge20_m014, cols = c("best", "lo", "hi"), names_to = "est")
box20_m014 <- boxplot(value ~ g_whoregion, piv20_m014, horizontal = TRUE, las = 1, cex.names = 0.5)
points(x = merge20_m014$cases,
       y = 1:6,
       col = "red",
       pch = 16)

piv20_f014 <- pivot_longer(merge20_f014, cols = c("best", "lo", "hi"), names_to = "est")
box20_f014 <- boxplot(value ~ g_whoregion, piv20_f014, horizontal = TRUE, las = 1, cex.names = 0.5)
points(x = merge20_f014$cases,
       y = 1:6,
       col = "red",
       pch = 16)

piv20_m15plus <- pivot_longer(merge20_m15plus, cols = c("best", "lo", "hi"), names_to = "est")
box20_m15plus <- boxplot(value ~ g_whoregion, piv20_m15plus, horizontal = TRUE, las = 1, cex.names = 0.5)
points(x = merge20_m15plus$cases,
       y = 1:6,
       col = "red",
       pch = 16)

piv20_f15plus <- pivot_longer(merge20_f15plus, cols = c("best", "lo", "hi"), names_to = "est")
box20_f15plus <- boxplot(value ~ g_whoregion, piv20_f15plus, horizontal = TRUE, las = 1, cex.names = 0.5)
points(x = merge20_f15plus$cases,
       y = 1:6,
       col = "red",
       pch = 16)

```

Creating comibned data frame comparing 2019 and 2020 data 

```{r}
#Age 04 side-by-side
sexM <- "male"
merg_m04 <- merge(pivtot_m04, piv20_m04, by = c("g_whoregion", "est"), all.x = TRUE)
colnames(merg_m04) <- c("g_whoregion", "est", "case_2019", "est_2019", "case_2020", "est_2020")
merg_m04 <- cbind(merg_m04, sexM)
colnames(merg_m04)[colnames(merg_m04) == "sexM"] <- "sex"

sexF <- "female"
merg_f04 <- merge(pivtot_f04, piv20_f04, by = c("g_whoregion", "est"), all.x = TRUE)
colnames(merg_f04) <- c("g_whoregion", "est", "case_2019", "est_2019", "case_2020", "est_2020")
merg_f04 <- cbind(merg_f04, sexF)
colnames(merg_f04)[colnames(merg_f04) == "sexF"] <- "sex"

merged_04 <- rbind(merg_m04, merg_f04)
merged_044 <- merged_04[, -c(3,5)]
long_04 <- pivot_longer(merged_044, cols = c("est_2019", "est_2020"))

gg_try04 <- ggplot(long_04, aes(x = g_whoregion, y = value, color = name)) + geom_boxplot() + facet_wrap(~long_04$sex)

#Age 5-14 side-by-side
sexM <- "male"
merg_m514 <- merge(pivtot_m514, piv20_m514, by = c("g_whoregion", "est"), all.x = TRUE)
colnames(merg_m514) <- c("g_whoregion", "est", "case_2019", "est_2019", "case_2020", "est_2020")
merg_m514 <- cbind(merg_m514, sexM)
colnames(merg_m514)[colnames(merg_m514) == "sexM"] <- "sex"

sexF <- "female"
merg_f514 <- merge(pivtot_f514, piv20_f514, by = c("g_whoregion", "est"), all.x = TRUE)
colnames(merg_f514) <- c("g_whoregion", "est", "case_2019", "est_2019", "case_2020", "est_2020")
merg_f514 <- cbind(merg_f514, sexF)
colnames(merg_f514)[colnames(merg_f514) == "sexF"] <- "sex"

merged_514 <- rbind(merg_m514, merg_f514)
merged_5144 <- merged_514[, -c(3,5)]
long_514 <- pivot_longer(merged_5144, cols = c("est_2019", "est_2020"))

gg_try514 <- ggplot(long_514, aes(x = g_whoregion, y = value, color = name)) + geom_boxplot() + facet_wrap(~long_514$sex)

#Age 15 plus side-by-side
sexM <- "male"
merg_m15plus <- merge(pivtot_m15plus, piv20_m15plus, by = c("g_whoregion", "est"), all.x = TRUE)
colnames(merg_m15plus) <- c("g_whoregion", "est", "case_2019", "est_2019", "case_2020", "est_2020")
merg_m15plus <- cbind(merg_m15plus, sexM)
colnames(merg_m15plus)[colnames(merg_m15plus) == "sexM"] <- "sex"

sexF <- "female"
merg_f15plus <- merge(pivtot_f15plus, piv20_f15plus, by = c("g_whoregion", "est"), all.x = TRUE)
colnames(merg_f15plus) <- c("g_whoregion", "est", "case_2019", "est_2019", "case_2020", "est_2020")
merg_f15plus <- cbind(merg_f15plus, sexF)
colnames(merg_f15plus)[colnames(merg_f15plus) == "sexF"] <- "sex"

merged_15plus <- rbind(merg_m15plus, merg_f15plus)
merged_15plus4 <- merged_15plus[, -c(3,5)]
long_15plus <- pivot_longer(merged_15plus4, cols = c("est_2019", "est_2020"))

gg_try15plus <- ggplot(long_15plus, aes(x = g_whoregion, y = value, color = name)) + geom_boxplot() + facet_wrap(~long_15plus$sex) 


```

Creating data frame to overlay the case data for each graph 

```{r}
cases_04 <- merged_04[, -c(2, 4,6)]
case_ready04 <- pivot_longer(cases_04, cols = c("case_2019", "case_2020"))

no_dups04 <- case_ready04[!duplicated(case_ready04),]

gg_try04 <- ggplot(long_04, aes(x = g_whoregion, y = value, color = name)) + geom_boxplot() + facet_wrap(~long_04$sex)


gg_alone <- ggplot(no_dups04, aes(x = g_whoregion, y = value, color = name)) + geom_point() + facet_wrap(~no_dups04$sex)

gg_try05 <- ggplot(long_04, aes(x = g_whoregion, y = value, color = name)) + geom_boxplot() + geom_point(data = no_dups04, aes(x = g_whoregion, y = value, color = name), inherit.aes = )  + facet_wrap(~long_04$sex)


###Trying again 
merged_05 <- merged_04[, -2]
incl_case <- pivot_longer(merged_05, cols = c("est_2019", "est_2020"))
incl_case2 <- pivot_longer(incl_case, cols = c("case_2019", "case_2020"), values_to = "cases", names_repair= "unique")
colnames(incl_case2) <- c("g_whoregion", "sex", "est", "est_value", "case", "case_value")

gg_incl04 <- ggplot(incl_case2, aes(x = g_whoregion, y = est_value, color = est)) + geom_boxplot() + geom_point(aes(x = g_whoregion, y = case_value, color = case)) + facet_wrap(~incl_case2$sex) + labs(title = "2019 vs 2020 estimate and notification data for 0-4 yrs")

gg_incl04

##Trying5-14 
merged_514_ready <- merged_514[, -2]
incl_case514 <- pivot_longer(merged_514_ready, cols = c("est_2019", "est_2020"))
incl_case5142 <- pivot_longer(incl_case514, cols = c("case_2019", "case_2020"), values_to = "cases", names_repair= "unique")
colnames(incl_case5142) <- c("g_whoregion", "sex", "est", "est_value", "case", "case_value")

gg_incl514 <- ggplot(incl_case5142, aes(x = g_whoregion, y = est_value, color = est)) + geom_boxplot() + geom_point(aes(x = g_whoregion, y = case_value, color = case)) + facet_wrap(~incl_case5142$sex) + labs(title = "2019 vs 2020 estimate and notification data for 5-14 yrs")
gg_incl514

#Trying 15plus
merged_15plus_ready <- merged_15plus[, -2]
incl_case15plus <- pivot_longer(merged_15plus_ready, cols = c("est_2019", "est_2020"))
incl_case15plus2 <- pivot_longer(incl_case15plus, cols = c("case_2019", "case_2020"), values_to = "cases", names_repair= "unique")
colnames(incl_case15plus2) <- c("g_whoregion", "sex", "est", "est_value", "case", "case_value")

gg_incl15plus <- ggplot(incl_case15plus2, aes(x = g_whoregion, y = est_value, color = est)) + geom_boxplot() + geom_point(aes(x = g_whoregion, y = case_value, color = case)) + facet_wrap(~incl_case15plus2$sex) + labs(title = "2019 vs 2020 estimate and notification data for 15plus yrs")
gg_incl15plus


```

