---
title: "All Countries Regional Data"
output: html_notebook
---

AIM: Create region by region analysis of male vs female for each age groups (0-4, 5-14, 0-14 and 15 plus) for all countries separated by region

```{r}
setwd("~/Desktop/AFP/modV3/data")
library(dplyr)
library(tidyverse)
library(tidyr)
library(forecast)
library(fpp2)
library(stringr)
library(magrittr)
library(ggplot2)

world <- read_csv("TB_notifications.csv")
tidyworld <- world[, c(1,3,5,6,100,103,104,113,115,118,119,128)]
world_2013 <- tidyworld %>% filter(year > 2012)
```

Organising the data by g_whoregion

```{r}
grouped_2013 <- group_by(world_2013, g_whoregion) %>% filter(year == 2013) %>% summarise(newrel_m04 = sum(na.omit(newrel_m04)), 
                                                                                         newrel_f04 = sum(na.omit(newrel_f04)),
                 newrel_m514 = sum(na.omit(newrel_m514)), newrel_f514 = sum(na.omit(newrel_f514)), 
                 newrel_m014 = sum(na.omit(newrel_m014)), newrel_f014 = sum(na.omit(newrel_f014)), 
                 newrel_m15plus = sum(na.omit(newrel_m15plus)), newrel_f15plus = sum(na.omit(newrel_f15plus))) %>% as.data.frame() %>% cbind(year = 2013)

grouped_2014 <- group_by(world_2013, g_whoregion) %>% filter(year == 2014) %>% summarise(newrel_m04 = sum(na.omit(newrel_m04)), 
                                                                                         newrel_f04 = sum(na.omit(newrel_f04)),
                 newrel_m514 = sum(na.omit(newrel_m514)), newrel_f514 = sum(na.omit(newrel_f514)), 
                 newrel_m014 = sum(na.omit(newrel_m014)), newrel_f014 = sum(na.omit(newrel_f014)), 
                 newrel_m15plus = sum(na.omit(newrel_m15plus)), newrel_f15plus = sum(na.omit(newrel_f15plus))) %>% as.data.frame() %>% cbind(year = 2014)

grouped_2015 <- group_by(world_2013, g_whoregion) %>% filter(year == 2015) %>% summarise(newrel_m04 = sum(na.omit(newrel_m04)), 
                                                                                         newrel_f04 = sum(na.omit(newrel_f04)),
                 newrel_m514 = sum(na.omit(newrel_m514)), newrel_f514 = sum(na.omit(newrel_f514)), 
                 newrel_m014 = sum(na.omit(newrel_m014)), newrel_f014 = sum(na.omit(newrel_f014)), 
                 newrel_m15plus = sum(na.omit(newrel_m15plus)), newrel_f15plus = sum(na.omit(newrel_f15plus))) %>% as.data.frame() %>% cbind(year = 2015)

grouped_2016 <- group_by(world_2013, g_whoregion) %>% filter(year == 2016) %>% summarise(newrel_m04 = sum(na.omit(newrel_m04)), 
                                                                                         newrel_f04 = sum(na.omit(newrel_f04)),
                 newrel_m514 = sum(na.omit(newrel_m514)), newrel_f514 = sum(na.omit(newrel_f514)), 
                 newrel_m014 = sum(na.omit(newrel_m014)), newrel_f014 = sum(na.omit(newrel_f014)), 
                 newrel_m15plus = sum(na.omit(newrel_m15plus)), newrel_f15plus = sum(na.omit(newrel_f15plus))) %>% as.data.frame() %>% cbind(year = 2016)

grouped_2017 <- group_by(world_2013, g_whoregion) %>% filter(year == 2017) %>% summarise(newrel_m04 = sum(na.omit(newrel_m04)), 
                                                                                         newrel_f04 = sum(na.omit(newrel_f04)),
                 newrel_m514 = sum(na.omit(newrel_m514)), newrel_f514 = sum(na.omit(newrel_f514)), 
                 newrel_m014 = sum(na.omit(newrel_m014)), newrel_f014 = sum(na.omit(newrel_f014)), 
                 newrel_m15plus = sum(na.omit(newrel_m15plus)), newrel_f15plus = sum(na.omit(newrel_f15plus))) %>% as.data.frame() %>% cbind(year = 2017)

grouped_2018 <- group_by(world_2013, g_whoregion) %>% filter(year == 2018) %>% summarise(newrel_m04 = sum(na.omit(newrel_m04)), 
                                                                                         newrel_f04 = sum(na.omit(newrel_f04)),
                 newrel_m514 = sum(na.omit(newrel_m514)), newrel_f514 = sum(na.omit(newrel_f514)), 
                 newrel_m014 = sum(na.omit(newrel_m014)), newrel_f014 = sum(na.omit(newrel_f014)), 
                 newrel_m15plus = sum(na.omit(newrel_m15plus)), newrel_f15plus = sum(na.omit(newrel_f15plus))) %>% as.data.frame() %>% cbind(year = 2018)

grouped_2019 <- group_by(world_2013, g_whoregion) %>% filter(year == 2019) %>% summarise(newrel_m04 = sum(na.omit(newrel_m04)), 
                                                                                         newrel_f04 = sum(na.omit(newrel_f04)),
                 newrel_m514 = sum(na.omit(newrel_m514)), newrel_f514 = sum(na.omit(newrel_f514)), 
                 newrel_m014 = sum(na.omit(newrel_m014)), newrel_f014 = sum(na.omit(newrel_f014)), 
                 newrel_m15plus = sum(na.omit(newrel_m15plus)), newrel_f15plus = sum(na.omit(newrel_f15plus))) %>% as.data.frame() %>% cbind(year = 2019)

grouped_2020 <- group_by(world_2013, g_whoregion) %>% filter(year == 2020) %>% summarise(newrel_m04 = sum(na.omit(newrel_m04)), 
                                                                                         newrel_f04 = sum(na.omit(newrel_f04)),
                 newrel_m514 = sum(na.omit(newrel_m514)), newrel_f514 = sum(na.omit(newrel_f514)), 
                 newrel_m014 = sum(na.omit(newrel_m014)), newrel_f014 = sum(na.omit(newrel_f014)), 
                 newrel_m15plus = sum(na.omit(newrel_m15plus)), newrel_f15plus = sum(na.omit(newrel_f15plus))) %>% as.data.frame() %>% cbind(year = 2020)

bind_world <- rbind(grouped_2013, grouped_2014, grouped_2015, grouped_2016, grouped_2017, grouped_2018, grouped_2019, grouped_2020)

bind_world <- bind_world[, c(1, 10, 2:9)]

arrange_world <- arrange(bind_world, g_whoregion)

##Including columns for total values 

mutate_world <- mutate(arrange_world, "newrel_tot04" = newrel_m04 + newrel_f04, "newrel_tot514" = newrel_m514 + newrel_f514, "newrel_tot014" = newrel_m014 + newrel_f014, "newrel_tot15plus" = newrel_m15plus + newrel_f15plus)

perc_world <- mutate(mutate_world, "perc_014" = 100 * (newrel_tot014/(newrel_tot014 + newrel_tot15plus)), "perc_youngkids" = 100 * (newrel_tot04/newrel_tot014))



```

Creating graphs for male vs female for 0-4 by g_whoregion

```{r}
afr_04 <- perc_world %>% filter(g_whoregion == "AFR") %>% select(newrel_m04, newrel_f04) %>% 
  t()
colnames(afr_04) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
afr_04 %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,30000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for ages 0-4 years in AFR")

amr_04 <- perc_world %>% filter(g_whoregion == "AMR") %>% select(newrel_m04, newrel_f04) %>% 
  t()
colnames(amr_04) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
amr_04 %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,3000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for ages 0-4 years in AMR")

emr_04 <- perc_world %>% filter(g_whoregion == "EMR") %>% select(newrel_m04, newrel_f04) %>% 
  t()
colnames(emr_04) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
emr_04 %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,20000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for ages 0-4 years in EMR")

eur_04 <- perc_world %>% filter(g_whoregion == "EUR") %>% select(newrel_m04, newrel_f04) %>% 
  t()
colnames(eur_04) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
eur_04 %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,3000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for ages 0-4 years in EUR")

sea_04 <- perc_world %>% filter(g_whoregion == "SEA") %>% select(newrel_m04, newrel_f04) %>% 
  t() 
colnames(sea_04) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
sea_04 %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,60000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for ages 0-4 years in SEA")

wpr_04 <- perc_world %>% filter(g_whoregion == "WPR") %>% select(newrel_m04, newrel_f04) %>% 
  t()
colnames(wpr_04) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
wpr_04 %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,20000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for ages 0-4 years in WPR")


```
Creating graphs for notifications in 5-14 years by g_whoregion

```{r}
afr_514 <- perc_world %>% filter(g_whoregion == "AFR") %>% select(newrel_m514, newrel_f514) %>% 
  t() 
colnames(afr_514) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
afr_514 %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,40000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for ages 0-514 years in AFR")

amr_514 <- perc_world %>% filter(g_whoregion == "AMR") %>% select(newrel_m514, newrel_f514) %>% 
  t() 
colnames(afr_514) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
amr_514 %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,4000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for ages 5-14 years in AMR")

emr_514 <- perc_world %>% filter(g_whoregion == "EMR") %>% select(newrel_m514, newrel_f514) %>% 
  t() 
colnames(emr_514) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
emr_514 %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,30000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for ages 5-14 years in EMR")

eur_514 <- perc_world %>% filter(g_whoregion == "EUR") %>% select(newrel_m514, newrel_f514) %>% 
  t()
colnames(eur_514) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
eur_514 %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,5000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for ages 5-14 years in EUR")

sea_514 <- perc_world %>% filter(g_whoregion == "SEA") %>% select(newrel_m514, newrel_f514) %>% 
  t() 
colnames(sea_514) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
sea_514 %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,100000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for ages 5-14 years in SEA")

wpr_514 <- perc_world %>% filter(g_whoregion == "WPR") %>% select(newrel_m514, newrel_f514) %>% 
  t()
colnames(wpr_514) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
wpr_514 %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,30000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for ages 5-14 years in WPR")
```
Creating plot for 0-14 

```{r}
afr_014 <- perc_world %>% filter(g_whoregion == "AFR") %>% select(newrel_m014, newrel_f014) %>% 
  t()
colnames(afr_014) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
afr_014 %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,70000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for ages 0-14 years in AFR")

amr_014 <- perc_world %>% filter(g_whoregion == "AMR") %>% select(newrel_m014, newrel_f014) %>% 
  t()
colnames(amr_014) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
amr_014 %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,6000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for ages 0-14 years in AMR")

emr_014 <- perc_world %>% filter(g_whoregion == "EMR") %>% select(newrel_m014, newrel_f014) %>% 
  t() 
colnames(emr_014) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
emr_014 %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,50000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for ages 0-14 years in EMR")

eur_014 <- perc_world %>% filter(g_whoregion == "EUR") %>% select(newrel_m014, newrel_f014) %>% 
  t() 
colnames(eur_014) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
eur_014 %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,8000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for ages 0-14 years in EUR")

sea_014 <- perc_world %>% filter(g_whoregion == "SEA") %>% select(newrel_m014, newrel_f014) %>% 
  t()
colnames(sea_014) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
sea_014 %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,150000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for ages 0-14 years in SEA")

wpr_014 <- perc_world %>% filter(g_whoregion == "WPR") %>% select(newrel_m014, newrel_f014) %>% 
  t() 
colnames(wpr_014) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
wpr_014 %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,50000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for ages 0-14 years in WPR")
```
Creating plot for 15 plus 

```{r}
afr_15plus <- perc_world %>% filter(g_whoregion == "AFR") %>% select(newrel_m15plus, newrel_f15plus) %>% 
  t() 
colnames(afr_15plus) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
afr_15plus %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,1000000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for ages 15plus years in AFR")

amr_15plus <- perc_world %>% filter(g_whoregion == "AMR") %>% select(newrel_m15plus, newrel_f15plus) %>% 
  t()
colnames(amr_15plus) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
amr_15plus %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,300000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for ages 15 plus years in AMR")

emr_15plus <- perc_world %>% filter(g_whoregion == "EMR") %>% select(newrel_m15plus, newrel_f15plus) %>% 
  t() 
colnames(emr_15plus) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
emr_15plus %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,500000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for ages 15plus years in EMR")

eur_15plus <- perc_world %>% filter(g_whoregion == "EUR") %>% select(newrel_m15plus, newrel_f15plus) %>% 
  t() 
colnames(eur_15plus) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
eur_15plus %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,200000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for ages 15plus years in EUR")

sea_15plus <- perc_world %>% filter(g_whoregion == "SEA") %>% select(newrel_m15plus, newrel_f15plus) %>% 
  t() 
colnames(sea_15plus) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
sea_15plus %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,2000000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for ages 15plus years in SEA")

wpr_15plus <- perc_world %>% filter(g_whoregion == "WPR") %>% select(newrel_m15plus, newrel_f15plus) %>% 
  t() 
colnames(wpr_15plus) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
wpr_15plus %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,1000000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for ages 15plus years in WPR")
```
Plotting total notifications over time 

```{r}
tot_world <- mutate(perc_world, "newrel_mtot" = newrel_m014 + newrel_m15plus, "newrel_ftot" = newrel_f014 + newrel_f15plus, "TOT" = newrel_mtot + newrel_ftot)

afr_tot <- tot_world %>% filter(g_whoregion == "AFR") %>% select(newrel_mtot, newrel_ftot) %>% 
  t() 
colnames(afr_tot) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
afr_tot %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,1000000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for all ages years in AFR")

amr_tot <- tot_world %>% filter(g_whoregion == "AMR") %>% select(newrel_mtot, newrel_ftot) %>% 
  t()
colnames(amr_tot) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
amr_tot %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,200000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for all ages years in AMR")

emr_tot <- tot_world %>% filter(g_whoregion == "EMR") %>% select(newrel_mtot, newrel_ftot) %>% 
  t() 
colnames(emr_tot) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
emr_tot %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,500000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for all ages years in EMR")

eur_tot <- tot_world %>% filter(g_whoregion == "EUR") %>% select(newrel_mtot, newrel_ftot) %>% 
  t()
colnames(eur_tot) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
eur_tot %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,200000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for all ages years in EUR")

sea_tot <- tot_world %>% filter(g_whoregion == "SEA") %>% select(newrel_mtot, newrel_ftot) %>% 
  t() 
colnames(sea_tot) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
sea_tot %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,3000000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for all ages years in SEA")

wpr_tot <- tot_world %>% filter(g_whoregion == "WPR") %>% select(newrel_mtot, newrel_ftot) %>% 
  t() 
colnames(wpr_tot) <- c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020")
wpr_tot %<>% barplot(col = c("skyblue", "seagreen1"), beside = TRUE, ylim = c(0,1500000), xlab = "year", ylab = "notifications") + title("Sex disaggregated notifications for all ages years in WPR")

```
```{r}
##Attempt at creating a forecast 

filt_afr04 <- perc_world %>% filter(g_whoregion == "AFR") %>% filter(year != 2020)

ts_afr04 <- ts(filt_afr04[, c(3)], start = 2013, frequency = 1)

arima_afr04 <- auto.arima(ts_afr04, d=1, D=1, stepwise = FALSE, approximation = FALSE, trace = TRUE)
print(summary(arima_afr04))
checkresiduals(arima_afr04)

fcst_afrm04 <- forecast(arima_afr04, h = 1)
autoplot(fcst)
sum_afrm04 <- print(summary(fcst))

####Attempt at creating function to produce predictions 

out_2020 <- function(df = tot_world, region){
        df %>% filter(year != 2020) %>% filter(g_whoregion == region) %>% return() }

arima_TB <- function(df = tot_world, group) {
        data1 <- df %>% select(group) %>% ts(start = 2013, frequency = 1) %>% auto.arima(d=1, D=1, stepwise = FALSE, approximation = FALSE, trace = TRUE) 
        print(summary(data1))
        FCST <- forecast(data1, h = 1)
        autoplot(FCST)
        print(summary(FCST))}

##AFRICA ESTIMATES 

afr_m04 <- out_2020(tot_world, "AFR") %>% arima_TB("newrel_m04") 
rownames(afr_m04) <- "afr_m04"

afr_f04 <- out_2020(tot_world, "AFR") %>% arima_TB("newrel_f04")
rownames(afr_f04) <- "afr_f04"

afr_m514 <- out_2020(tot_world, "AFR") %>% arima_TB("newrel_m514")
rownames(afr_m514) <- "afr_m514"

afr_f514 <- out_2020(tot_world, "AFR") %>% arima_TB("newrel_f514")
rownames(afr_f514) <- "afr_f514"

afr_m014 <- out_2020(tot_world, "AFR") %>% arima_TB("newrel_m014")
rownames(afr_m014) <- "afr_m014"

afr_f014 <- out_2020(tot_world, "AFR") %>% arima_TB("newrel_f014")
rownames(afr_f014) <- "afr_f014"

afr_m15plus <- out_2020(tot_world, "AFR") %>% arima_TB("newrel_m15plus")
rownames(afr_m15plus) <- "afr_m15plus"

afr_f15plus <- out_2020(tot_world, "AFR") %>% arima_TB("newrel_f15plus")
rownames(afr_f15plus) <- "afr_f15plus"

afr_estimates <- rbind(afr_m04, afr_f04, afr_m514, afr_f514, afr_m014, afr_f014, afr_m15plus, afr_f15plus)


#SEA predictions 
sea_m04 <- out_2020(tot_world, "SEA") %>% arima_TB("newrel_m04") 
rownames(sea_m04) <- "sea_m04"

sea_f04 <- out_2020(tot_world, "SEA") %>% arima_TB("newrel_f04")
rownames(sea_f04) <- "sea_f04"

sea_m514 <- out_2020(tot_world, "SEA") %>% arima_TB("newrel_m514")
rownames(sea_m514) <- "sea_m514"

sea_f514 <- out_2020(tot_world, "SEA") %>% arima_TB("newrel_f514")
rownames(sea_f514) <- "sea_f514"

sea_m014 <- out_2020(tot_world, "SEA") %>% arima_TB("newrel_m014")
rownames(sea_m014) <- "sea_m014"

sea_f014 <- out_2020(tot_world, "SEA") %>% arima_TB("newrel_f014")
rownames(sea_f014) <- "sea_f014"

sea_m15plus <- out_2020(tot_world, "SEA") %>% arima_TB("newrel_m15plus")
rownames(sea_m15plus) <- "sea_m15plus"

sea_f15plus <- out_2020(tot_world, "SEA") %>% arima_TB("newrel_f15plus")
rownames(sea_f15plus) <- "sea_f15plus"

sea_estimates <- rbind(sea_m04, sea_f04, sea_m514, sea_f514, sea_m014, sea_f014, sea_m15plus, sea_f15plus)

#WPR estimates 

wpr_m04 <- out_2020(tot_world, "WPR") %>% arima_TB("newrel_m04") 
rownames(wpr_m04) <- "wpr_m04"

wpr_f04 <- out_2020(tot_world, "WPR") %>% arima_TB("newrel_f04")
rownames(wpr_f04) <- "wpr_f04"

wpr_m514 <- out_2020(tot_world, "WPR") %>% arima_TB("newrel_m514")
rownames(wpr_m514) <- "wpr_m514"

wpr_f514 <- out_2020(tot_world, "WPR") %>% arima_TB("newrel_f514")
rownames(wpr_f514) <- "wpr_f514"

wpr_m014 <- out_2020(tot_world, "WPR") %>% arima_TB("newrel_m014")
rownames(wpr_m014) <- "wpr_m014"

wpr_f014 <- out_2020(tot_world, "WPR") %>% arima_TB("newrel_f014")
rownames(wpr_f014) <- "wpr_f014"

wpr_m15plus <- out_2020(tot_world, "WPR") %>% arima_TB("newrel_m15plus")
rownames(wpr_m15plus) <- "wpr_m15plus"

wpr_f15plus <- out_2020(tot_world, "WPR") %>% arima_TB("newrel_f15plus")
rownames(wpr_f15plus) <- "wpr_f15plus"

wpr_estimates <- rbind(wpr_m04, wpr_f04, wpr_m514, wpr_f514, wpr_m014, wpr_f014, wpr_m15plus, wpr_f15plus)

#EUR Estimates

eur_m04 <- out_2020(tot_world, "EUR") %>% arima_TB("newrel_m04") 
rownames(eur_m04) <- "eur_m04"

eur_f04 <- out_2020(tot_world, "EUR") %>% arima_TB("newrel_f04")
rownames(eur_f04) <- "eur_f04"

eur_m514 <- out_2020(tot_world, "EUR") %>% arima_TB("newrel_m514")
rownames(eur_m514) <- "eur_m514"

eur_f514 <- out_2020(tot_world, "EUR") %>% arima_TB("newrel_f514")
rownames(eur_f514) <- "eur_f514"

eur_m014 <- out_2020(tot_world, "EUR") %>% arima_TB("newrel_m014")
rownames(eur_m014) <- "eur_m014"

eur_f014 <- out_2020(tot_world, "EUR") %>% arima_TB("newrel_f014")
rownames(eur_f014) <- "eur_f014"

eur_m15plus <- out_2020(tot_world, "EUR") %>% arima_TB("newrel_m15plus")
rownames(eur_m15plus) <- "eur_m15plus"

eur_f15plus <- out_2020(tot_world, "EUR") %>% arima_TB("newrel_f15plus")
rownames(eur_f15plus) <- "eur_f15plus"

eur_estimates <- rbind(eur_m04, eur_f04, eur_m514, eur_f514, eur_m014, eur_f014, eur_m15plus, eur_f15plus)

#AMR Estimates

emr_m04 <- out_2020(tot_world, "EMR") %>% arima_TB("newrel_m04") 
rownames(emr_m04) <- "emr_m04"

emr_f04 <- out_2020(tot_world, "EMR") %>% arima_TB("newrel_f04")
rownames(emr_f04) <- "emr_f04"

emr_m514 <- out_2020(tot_world, "EMR") %>% arima_TB("newrel_m514")
rownames(emr_m514) <- "emr_m514"

emr_f514 <- out_2020(tot_world, "EMR") %>% arima_TB("newrel_f514")
rownames(emr_f514) <- "emr_f514"

emr_m014 <- out_2020(tot_world, "EMR") %>% arima_TB("newrel_m014")
rownames(emr_m014) <- "emr_m014"

emr_f014 <- out_2020(tot_world, "EMR") %>% arima_TB("newrel_f014")
rownames(emr_f014) <- "emr_f014"

emr_m15plus <- out_2020(tot_world, "EMR") %>% arima_TB("newrel_m15plus")
rownames(emr_m15plus) <- "emr_m15plus"

emr_f15plus <- out_2020(tot_world, "EMR") %>% arima_TB("newrel_f15plus")
rownames(emr_f15plus) <- "emr_f15plus"

emr_estimates <- rbind(emr_m04, emr_f04, emr_m514, emr_f514, emr_m014, emr_f014, emr_m15plus, emr_f15plus)

#WPR Estimates

wpr_m04 <- out_2020(tot_world, "WPR") %>% arima_TB("newrel_m04") 
rownames(wpr_m04) <- "wpr_m04"

wpr_f04 <- out_2020(tot_world, "WPR") %>% arima_TB("newrel_f04")
rownames(wpr_f04) <- "wpr_f04"

wpr_m514 <- out_2020(tot_world, "WPR") %>% arima_TB("newrel_m514")
rownames(wpr_m514) <- "wpr_m514"

wpr_f514 <- out_2020(tot_world, "WPR") %>% arima_TB("newrel_f514")
rownames(wpr_f514) <- "wpr_f514"

wpr_m014 <- out_2020(tot_world, "WPR") %>% arima_TB("newrel_m014")
rownames(wpr_m014) <- "wpr_m014"

wpr_f014 <- out_2020(tot_world, "WPR") %>% arima_TB("newrel_f014")
rownames(wpr_f014) <- "wpr_f014"

wpr_m15plus <- out_2020(tot_world, "WPR") %>% arima_TB("newrel_m15plus")
rownames(wpr_m15plus) <- "wpr_m15plus"

wpr_f15plus <- out_2020(tot_world, "WPR") %>% arima_TB("newrel_f15plus")
rownames(wpr_f15plus) <- "wpr_f15plus"

wpr_estimates <- rbind(wpr_m04, wpr_f04, wpr_m514, wpr_f514, wpr_m014, wpr_f014, wpr_m15plus, wpr_f15plus)

#AMR Estimates

amr_m04 <- out_2020(tot_world, "AMR") %>% arima_TB("newrel_m04") 
rownames(amr_m04) <- "amr_m04"

amr_f04 <- out_2020(tot_world, "AMR") %>% arima_TB("newrel_f04")
rownames(amr_f04) <- "amr_f04"

amr_m514 <- out_2020(tot_world, "AMR") %>% arima_TB("newrel_m514")
rownames(amr_m514) <- "amr_m514"

amr_f514 <- out_2020(tot_world, "AMR") %>% arima_TB("newrel_f514")
rownames(amr_f514) <- "amr_f514"

amr_m014 <- out_2020(tot_world, "AMR") %>% arima_TB("newrel_m014")
rownames(amr_m014) <- "amr_m014"

amr_f014 <- out_2020(tot_world, "AMR") %>% arima_TB("newrel_f014")
rownames(amr_f014) <- "amr_f014"

amr_m15plus <- out_2020(tot_world, "AMR") %>% arima_TB("newrel_m15plus")
rownames(amr_m15plus) <- "amr_m15plus"

amr_f15plus <- out_2020(tot_world, "AMR") %>% arima_TB("newrel_f15plus")
rownames(amr_f15plus) <- "amr_f15plus"

amr_estimates <- rbind(amr_m04, amr_f04, amr_m514, amr_f514, amr_m014, amr_f014, amr_m15plus, amr_f15plus)

```
Combining the data for 2020 with the model estimates 

```{r}
##AFR difference calculations 
afr_2020 <- tot_world %>% filter(year == 2020) %>% filter(g_whoregion == "AFR") %>% t() 
afr_2020 <- as.data.frame(afr_2020[c(3:10), ])

rownames(afr_2020) <- c("afr_m04", "afr_f04", "afr_m514", "afr_f514", "afr_m014", "afr_f014", "afr_m15plus", "afr_f15plus")
colnames(afr_2020) <- "notif_2020"

est_afr_2020 <- cbind(afr_2020, afr_estimates)
colnames(est_afr_2020) <- c("notif_2020", "est_2020", "Lo_80", "Hi_80", "Lo_95", "Hi_95")
est_afr_2020$notif_2020 <- as.numeric(est_afr_2020$notif_2020)

dif_afr <- mutate(est_afr_2020, "Difference" = notif_2020 - est_2020, "afr_perc" = 100*(Difference/est_2020))

##SEA difference calculations 
sea_2020 <- tot_world %>% filter(year == 2020) %>% filter(g_whoregion == "SEA") %>% t() 
sea_2020 <- as.data.frame(sea_2020[c(3:10), ])

rownames(sea_2020) <- c("sea_m04", "sea_f04", "sea_m514", "sea_f514", "sea_m014", "sea_f014", "sea_m15plus", "sea_f15plus")
colnames(sea_2020) <- "notif_2020"
est_sea_2020 <- cbind(sea_2020, sea_estimates)
colnames(est_sea_2020) <- c("notif_2020", "est_2020", "Lo_80", "Hi_80", "Lo_95", "Hi_95")
est_sea_2020$notif_2020 <- as.numeric(est_sea_2020$notif_2020)

dif_sea <- mutate(est_sea_2020, "Difference" = notif_2020 - est_2020, "sea_perc" = 100*(Difference/est_2020))

#WPR difference calculations 
wpr_2020 <- tot_world %>% filter(year == 2020) %>% filter(g_whoregion == "WPR") %>% t() 
wpr_2020 <- as.data.frame(wpr_2020[c(3:10), ])

rownames(wpr_2020) <- c("wpr_m04", "wpr_f04", "wpr_m514", "wpr_f514", "wpr_m014", "wpr_f014", "wpr_m15plus", "wpr_f15plus")
colnames(wpr_2020) <- "wpr_2020"
est_wpr_2020 <- cbind(wpr_2020, wpr_estimates)
colnames(est_wpr_2020) <- c("notif_2020", "est_2020", "Lo_80", "Hi_80", "Lo_95", "Hi_95")
est_wpr_2020$notif_2020 <- as.numeric(est_wpr_2020$notif_2020)

dif_wpr <- mutate(est_wpr_2020, "Difference" = notif_2020 - est_2020, "wpr_perc" = 100*(Difference/est_2020))

#WPR difference calculations 
eur_2020 <- tot_world %>% filter(year == 2020) %>% filter(g_whoregion == "EUR") %>% t() 
eur_2020 <- as.data.frame(eur_2020[c(3:10), ])

rownames(eur_2020) <- c("eur_m04", "eur_f04", "eur_m514", "eur_f514", "eur_m014", "eur_f014", "eur_m15plus", "eur_f15plus")
colnames(eur_2020) <- "eur_2020"
est_eur_2020 <- cbind(eur_2020, eur_estimates)
colnames(est_eur_2020) <- c("notif_2020", "est_2020", "Lo_80", "Hi_80", "Lo_95", "Hi_95")
est_eur_2020$notif_2020 <- as.numeric(est_eur_2020$notif_2020)

dif_eur <- mutate(est_eur_2020, "Difference" = notif_2020 - est_2020, "eur_perc" = 100*(Difference/est_2020)) 

#AMR difference calculations
amr_2020 <- tot_world %>% filter(year == 2020) %>% filter(g_whoregion == "AMR") %>% t() 
amr_2020 <- as.data.frame(amr_2020[c(3:10), ])

rownames(amr_2020) <- c("amr_m04", "amr_f04", "amr_m514", "amr_f514", "amr_m014", "amr_f014", "amr_m15plus", "amr_f15plus")
colnames(eur_2020) <- "amr_2020"
est_amr_2020 <- cbind(amr_2020, amr_estimates)
colnames(est_amr_2020) <- c("notif_2020", "est_2020", "Lo_80", "Hi_80", "Lo_95", "Hi_95")
est_amr_2020$notif_2020 <- as.numeric(est_amr_2020$notif_2020)

dif_amr <- mutate(est_amr_2020, "Difference" = notif_2020 - est_2020, "amr_perc" = 100*(Difference/est_2020)) 

#EMR difference calculations
emr_2020 <- tot_world %>% filter(year == 2020) %>% filter(g_whoregion == "EMR") %>% t() 
emr_2020 <- as.data.frame(emr_2020[c(3:10), ])

rownames(emr_2020) <- c("emr_m04", "emr_f04", "emr_m514", "emr_f514", "emr_m014", "emr_f014", "emr_m15plus", "emr_f15plus")
colnames(emr_2020) <- "emr_2020"
est_emr_2020 <- cbind(emr_2020, emr_estimates)
colnames(est_emr_2020) <- c("notif_2020", "est_2020", "Lo_80", "Hi_80", "Lo_95", "Hi_95")
est_emr_2020$notif_2020 <- as.numeric(est_emr_2020$notif_2020)

dif_emr <- mutate(est_emr_2020, "Difference" = notif_2020 - est_2020, "emr_perc" = 100*(Difference/est_2020)) 

#Combined data frame with difference data 
combined_dif <- data.frame(dif_afr[, c(7,8)], dif_amr[,c(7,8)], dif_emr[, c(7,8)], dif_eur[,c(7:8)], dif_sea[,c(7:8)], dif_wpr[,c(7:8)])
combined_dif$group <- as.vector(rownames(combined_dif))
combined_dif$group <- c("m04", "f04", "m514", "f514", "m014", "f014", "m15plus", "f15plus")
rownames(combined_dif) <- c(1:8)
combined_dif <- combined_dif[, c(13,1:12)]

colnames(combined_dif) <- c("group", "AFR_dif", "AFR_perc", "AMR_dif", "AMR_perc", "EMR_dif", "EMR_perc", "EUR_dif", "EUR_perc", "SEA_dif", "SEA_perc", "WPR_dif", "WPR_perc")

#isolating only the percentage data to be able to plot a bar plot 
bar_data <- combined_dif[, c(1,3,5,7,9,11,13)]
bar_newgroup <- str_split_fixed(bar_data$group, "", 2)
bar_data2 <- cbind(bar_data, bar_newgroup)
colnames(bar_data2) <- c("group", "AFR", "AMR", "EMR", "EUR", "SEA", "WPR", "sex", "age_group")
bar_data2 <- bar_data2[, c(9,8,2:7)]


piv_dif <- pivot_longer(bar_data2, cols = c("AFR", "AMR", "EMR", "EUR", "SEA", "WPR"), names_to = "g_whoregion", values_to = "value")

library(dplyr)
library(ggplot2)
piv_three <- filter(piv_dif, age_group != "014")

##Attempt at drawing plots  including 0-14 
arima_dif <- ggplot(piv_dif, aes(x = g_whoregion, y = value, fill = sex)) + facet_wrap(~piv_dif$age_group) + geom_bar(stat = "identity", position = "dodge")

##Attempt excluding 0-14 
piv_copy <- piv_three
piv_copy$age_group <- factor(piv_copy$age_group, levels = c("04", "514", "15plus"))
arima_copy <- ggplot(piv_copy, aes(x = g_whoregion, y = value, fill = sex)) + facet_wrap(~piv_copy$age_group) + geom_bar(stat = "identity", position = "dodge")
arima_copy

arima_three <- ggplot(piv_three, aes(x = g_whoregion, y = value, fill = sex)) + facet_wrap(~piv_three$age_group) + geom_bar(stat = "identity", position = "dodge")
arima_three
    
``` 



```{r}
#Attempt at the forecasting models 
#Rearranging data for 0-4 males 

males_04 <- select(perc_world, c(g_whoregion, year, newrel_m04)) 
piv_na <- pivot_wider(males_04, names_from = "year", values_from = "newrel_m04")
piv_na$`2020` <- NA
males_back <- pivot_longer(piv_na, cols = c(as.vector(colnames(piv_na[,2:9]))), names_to = "year")
males_back$year <- as.numeric(males_back$year)
males_no_pivot <- males_04
males_pivot <- pivot_wider(males_04, names_from = "g_whoregion", values_from = "newrel_m04")

select(afr_m04, "Point Forecast")

fore2020 <- function(df){
  a <- select(df, "Point Forecast")
  b <- "2020"
  colnames(a) <- "Number"
  rownames(a) <- NULL
  a$Year <- b
  return(a)
}

#males 04 
fore_afrm04 <- fore2020(afr_m04)
fore_amrm04 <- fore2020(amr_m04)
fore_emrm04 <- fore2020(emr_m04)
fore_eurm04 <- fore2020(eur_m04)
fore_seam04 <- fore2020(sea_m04)
fore_wprm04 <- fore2020(wpr_m04)

bound_fore <- cbind(fore_afrm04, fore_amrm04$Number, fore_emrm04$Number, fore_eurm04$Number, fore_seam04$Number, fore_wprm04$Number)

colnames(bound_fore) <- c("AFR", "Year", "AMR", "EMR", "EUR", "SEA", "WPR")
bound_fore <- bound_fore[, c(2, 1, 3:7)]

#females04
fore_afrf04 <- fore2020(afr_f04)
fore_amrf04 <- fore2020(amr_f04)
fore_emrf04 <- fore2020(emr_f04)
fore_eurf04 <- fore2020(eur_f04)
fore_seaf04 <- fore2020(sea_f04)
fore_wprf04 <- fore2020(wpr_f04)

bound_f04 <- cbind(fore_afrf04, fore_amrf04$Number, fore_emrf04$Number, fore_eurf04$Number, fore_seaf04$Number, fore_wprf04$Number)

colnames(bound_f04) <- c("AFR", "Year", "AMR", "EMR", "EUR", "SEA", "WPR")
bound_f04 <- bound_f04[, c(2, 1, 3:7)]

#males 514 
fore_afrm514 <- fore2020(afr_m514)
fore_amrm514 <- fore2020(amr_m514)
fore_emrm514 <- fore2020(emr_m514)
fore_eurm514 <- fore2020(eur_m514)
fore_seam514 <- fore2020(sea_m514)
fore_wprm514 <- fore2020(wpr_m514)

bound_m514 <- cbind(fore_afrm514, fore_amrm514$Number, fore_emrm514$Number, fore_eurm514$Number, fore_seam514$Number, fore_wprm514$Number)

colnames(bound_m514) <- c("AFR", "Year", "AMR", "EMR", "EUR", "SEA", "WPR")
bound_m514 <- bound_m514[, c(2, 1, 3:7)]

#females 514 
fore_afrf514 <- fore2020(afr_f514)
fore_amrf514 <- fore2020(amr_f514)
fore_emrf514 <- fore2020(emr_f514)
fore_eurf514 <- fore2020(eur_f514)
fore_seaf514 <- fore2020(sea_f514)
fore_wprf514 <- fore2020(wpr_f514)

bound_f514 <- cbind(fore_afrf514, fore_amrf514$Number, fore_emrf514$Number, fore_eurf514$Number, fore_seaf514$Number, fore_wprf514$Number)

colnames(bound_f514) <- c("AFR", "Year", "AMR", "EMR", "EUR", "SEA", "WPR")
bound_f514 <- bound_f514[, c(2, 1, 3:7)]

#males 15plus 
fore_afrm15plus <- fore2020(afr_m15plus)
fore_amrm15plus <- fore2020(amr_m15plus)
fore_emrm15plus <- fore2020(emr_m15plus)
fore_eurm15plus <- fore2020(eur_m15plus)
fore_seam15plus <- fore2020(sea_m15plus)
fore_wprm15plus <- fore2020(wpr_m15plus)

bound_m15plus <- cbind(fore_afrm15plus, fore_amrm15plus$Number, fore_emrm15plus$Number, fore_eurm15plus$Number, fore_seam15plus$Number, fore_wprm15plus$Number)

colnames(bound_m15plus) <- c("AFR", "Year", "AMR", "EMR", "EUR", "SEA", "WPR")
bound_m15plus <- bound_m15plus[, c(2, 1, 3:7)]

#females 15plus 
fore_afrf15plus <- fore2020(afr_f15plus)
fore_amrf15plus <- fore2020(amr_f15plus)
fore_emrf15plus <- fore2020(emr_f15plus)
fore_eurf15plus <- fore2020(eur_f15plus)
fore_seaf15plus <- fore2020(sea_f15plus)
fore_wprf15plus <- fore2020(wpr_f15plus)

bound_f15plus <- cbind(fore_afrf15plus, fore_amrf15plus$Number, fore_emrf15plus$Number, fore_eurf15plus$Number, fore_seaf15plus$Number, fore_wprf15plus$Number)

colnames(bound_f15plus) <- c("AFR", "Year", "AMR", "EMR", "EUR", "SEA", "WPR")
bound_f15plus <- bound_f15plus[, c(2, 1, 3:7)]


```

Attempt 2 at creating the time series analyses 

```{r}
#males04 plot
males_04 <- select(perc_world, c(g_whoregion, year, newrel_m04)) 
gg_males04 <- ggplot(males_04, aes(x = year, y = newrel_m04, col = g_whoregion)) + geom_line() + geom_point(x = 2020, y = 27043, col = "red") + geom_point(x = 2020, y = 2062, col = "brown") + geom_point(x = 2020, y = 17243.17, col = "green") + geom_point(x = 2020, y = 1465, col = "turquoise2") + geom_point(x = 2020, y = 58951.83, col = "blue") + geom_point(x = 2020, y = 12558, col = "pink") + scale_y_continuous(limits = c(0, 60000))

#females 04 plot
females_04 <- select(perc_world, c(g_whoregion, year, newrel_f04)) 
gg_females04 <- ggplot(females_04, aes(x = year, y = newrel_f04, col = g_whoregion)) + geom_line() + geom_point(x = 2020, y = 23790, col = "red") + geom_point(x = 2020, y = 1776, col = "brown") + geom_point(x = 2020, y = 13286.17, col = "green") + geom_point(x = 2020, y = 1269, col = "turquoise2") + geom_point(x = 2020, y = 43694, col = "blue") + geom_point(x = 2020, y = 10140, col = "pink") + scale_y_continuous(limits = c(0, 50000))

#males 514 plot 
males_514 <- select(perc_world, c(g_whoregion, year, newrel_m514)) 
gg_males514 <- ggplot(males_514, aes(x = year, y = newrel_m514, col = g_whoregion)) + geom_line() + geom_point(x = 2020, y = 32352, col = "red") + geom_point(x = 2020, y = 2826, col = "brown") + geom_point(x = 2020, y = 18620, col = "green") + geom_point(x = 2020, y = 3057, col = "turquoise2") + geom_point(x = 2020, y = 82535, col = "blue") + geom_point(x = 2020, y = 19606, col = "pink") + scale_y_continuous(limits = c(0, 90000))

#females514
females_514 <- select(perc_world, c(g_whoregion, year, newrel_f514)) 
gg_females514 <- ggplot(females_514, aes(x = year, y = newrel_f514, col = g_whoregion)) + geom_line() + geom_point(x = 2020, y = 32411, col = "red") + geom_point(x = 2020, y = 2897, col = "brown") + geom_point(x = 2020, y = 21632, col = "green") + geom_point(x = 2020, y = 2953, col = "turquoise2") + geom_point(x = 2020, y = 87086, col = "blue") + geom_point(x = 2020, y = 17500, col = "pink") + scale_y_continuous(limits = c(0, 100000))

#males 15 plus plot 
males_15plus <- select(perc_world, c(g_whoregion, year, newrel_m15plus)) 
gg_males15plus <- ggplot(males_15plus, aes(x = year, y = newrel_m15plus, col = g_whoregion)) + geom_line() + geom_point(x = 2020, y = 661953, col = "red") + geom_point(x = 2020, y = 154305.3, col = "brown") + geom_point(x = 2020, y = 226294, col = "green") + geom_point(x = 2020, y = 129819.7, col = "turquoise2") + geom_point(x = 2020, y = 1931341, col = "blue") + geom_point(x = 2020, y = 891849, col = "pink") + scale_y_continuous(limits = c(0, 2000000))

#females 15 plus plot 
females_15plus <- select(perc_world, c(g_whoregion, year, newrel_f15plus)) 
gg_females15plus <- ggplot(females_15plus, aes(x = year, y = newrel_f15plus, col = g_whoregion)) + geom_line() + geom_point(x = 2020, y = 426790, col = "red") + geom_point(x = 2020, y = 77417, col = "brown") + geom_point(x = 2020, y = 201386, col = "green") + geom_point(x = 2020, y = 66222.5, col = "turquoise2") + geom_point(x = 2020, y = 1182645, col = "blue") + geom_point(x = 2020, y = 435651, col = "pink") + scale_y_continuous(limits = c(0, 1200000))

```

